
%
% Chapter 5 of my master thesis:
% The analysis part begins
%

\chapter{A locally convex topology for the Gutt star product}

We have finished the algebraic part of this work, except for one little 
lemma concerning the Hopf theoretic chapter. Our next goal is setting up a 
locally convex topology on the symmetric tensor algebra, in which the Gutt 
star product will be continuous. At the beginning of this chapter, we will 
first give a motivation why the setting of locally convex algebras is 
convenient and necessary. In the second section, we will briefly recall the 
most important things on locally convex algebras and introduce the topology 
which we will work with. In the third section, the core of this chapter, the 
continuity of the star product and the analytic dependence on the formal 
parameter are proven. We also show that continuous representations of Lie 
algebras lift to  those of the deformed symmetric algebra and that our 
construction is in fact functorial. Part four treats the case when the formal 
parameter $z = 1$ and hence talks about a locally convex topology on universal 
enveloping algebras. We will show, that our topology is ''optimal'' in a 
specific sense.



\section{Why locally convex?}
\label{sec:chap5_Prelim}

The first question one could ask is why we want the observable algebra 
to be a \textit{locally convex} one. One can think of very different types of 
topologies and most of them would be nicer than a locally convex setting: we 
could think of locally multiplicatively convex algebras, Banach algebras, 
$C^*$- or even von Neumann algebras. All of them have much more structure than 
just locally convex algebras. We would have an entire holomorphic calculus 
within our algebra if we assumed it to be locally m-convex, or even a 
continuous one if we wanted it to be $C^*$.


The reason for our choice is that, in general, all these nice features are 
simply not there. Quantum mechanics tells us that even for the simplest systems 
the algebra made up by the space and momentum operators $\hat{q}$ and $\hat{p}$ 
can not be locally m-convex and hence not Banach or $C^*$.
\begin{proposition}
	\label{Prop:LCAna:QMnotLMC}
	Let $\mathcal{A}$ be a unital associative algebra which contains the 
	quantum mechanical observables $\hat{q}$ and $\hat{p}$ and in which 
	the canonical commutation relation
	\begin{equation*}
		[\hat{q}, \hat{p}]
		=
		i \hbar \Unit
	\end{equation*}
	is fulfilled. Then the only submultiplicative seminorm on it is 0.
\end{proposition}
\begin{proof}
	First, we need to show a little lemma:
	\begin{lemma}
		\label{Lemma:LCAna:NotLMCHelp}
		In the given algebra, we have for $n \in \mathbb{N}$
		\begin{equation}
			\label{LCAna:NotLMCHelp}
			\left( \ad_{\hat{q}} \right)^n (\hat{p}^n)
			=
			(i \hbar)^n n! \Unit.
		\end{equation}
	\end{lemma}
	\begin{subproof}
		To show it, we use the fact that for $a \in \mathcal{A}$ the 
		operator $\ad_a$ is a derivation. This is always true for the 
		commutator Lie algebra of an associative algebra, since for 
		$a, b, c \in \mathcal{A}$ we have
		\begin{equation*}
			[a, bc]
			=
			a b c - b c a
			=
			a b c - b a c + b a c - b c a
			=
			[a, b] c + b [a, c].
		\end{equation*}
		For $n = 1$, Equation \eqref{LCAna:NotLMCHelp} is 
		certainly true. So let's look at the step $n \rightarrow n+1$.
		We make use of the derivation property and have
		\begin{align*}
			\left( \ad_{\hat{q}} \right)^{n+1}
			\left( \hat{p}^{n+1} \right)
			& =
			\left( \ad_{\hat{q}} \right)^{n}
			\left(
				i \hbar \hat{p}^n
				+
				\hat{p} 
				\ad_{\hat{q}} \left( \hat{p}^n \right)
			\right)
			\\
			& =
			(i \hbar)^{n + 1} n!
			+
			\left( \ad_{\hat{q}} \right)^{n}
			\left(
				\hat{p}
				\ad_{\hat{q}} \left( \hat{p}^n \right)
			\right)
			\\
			& =
			(i \hbar)^{n + 1} n!
			+
			\left( \ad_{\hat{q}} \right)^{n-1}
			\left(
				[\hat{q}, \hat{p}]
				\ad_{\hat{q}} \left( \hat{p}^n \right)
				+
				\hat{p}
				\left( \ad_{\hat{q}} \right)^2
				\left( \hat{p}^n \right)
			\right)
			\\
			& =
			(i \hbar)^{n + 1} n!
			+
			i \hbar
			\left( \ad_{\hat{q}} \right)^{n}
			\left( \hat{p}^n \right)
			+
			\left( \ad_{\hat{q}} \right)^{n-1}
			\left(
				\hat{p}
				\left( \ad_{\hat{q}} \right)^2
				\left( \hat{p}^n \right)
			\right)
			\\
			& =
			2 (i \hbar)^{n+1} n!
			+
			\left( \ad_{\hat{q}} \right)^{n-1}
			\left(
				\hat{p}
				\left( \ad_{\hat{q}} \right)^2
				\left( \hat{p}^n \right)
			\right)
			\\
			& \ot{($*$)}{=} 
			\quad \vdots
			\\
			& =
			n (i \hbar)^{n+1} n!
			+
			\ad_{\hat{q}}
			\left(
				\hat{p}
				\left( \ad_{\hat{q}} \right)^n
				\left( \hat{p}^n \right)
			\right)
			\\
			& =
			n (i \hbar)^{n+1} n!
			+
			i \hbar (i \hbar)^n n!
			\\
			& =
			(i \hbar)^{n + 1} (n + 1)!.
		\end{align*}
		At ($*$), we actually used another statement which is to be 
		proven by induction over $k$ and says
		\begin{equation*}
			\left( \ad_{\hat{q}} \right)^{n + 1}
			\left( \hat{p}^{n + 1} \right)
			=
			k (i \hbar)^{n + 1} n!
			+
			\left( \ad_{\hat{q}} \right)^{n + 1 - k}
			\left(
				\hat{p}
				\left( \ad_{\hat{q}} \right)^k
				\left( \hat{p}^n \right)
			\right).
		\end{equation*}
		Since this proof is analogous to the first lines of the 
		computation before, we omit it here and the lemma is proven.
	\end{subproof}	
	Now we can go on with the actual proof. Let $\norm{\cdot}$ be a 
	submultiplicative seminorm. Then we see from Equation 
	\eqref{LCAna:NotLMCHelp} that
	\begin{equation*}
		\norm{
			\left( \ad_{\hat{q}} \right)^n
			(\hat{p}^n)
		}
		=
		|\hbar|^n n! \norm{ \Unit }.
	\end{equation*}
	On the other hand, we have
	\begin{align*}
		\norm{
			\left( \ad_{\hat{q}} \right)^n
			(\hat{p}^n)
		}
		& =
		\norm{
			\hat{q}
			\left( \ad_{\hat{q}} \right)^{n-1}
			(\hat{p}^n)
			-
			\left( \ad_{\hat{q}} \right)^{n-1}
			(\hat{p}^n)
			\hat{q}
		}
		\\
		& \leq
		2 \norm{\hat{q}}
		\norm{
			\left( \ad_{\hat{q}} \right)^{n-1}
			(\hat{p}^n)
		}
		\\
		& \leq
		\quad \vdots
		\\
		& \leq
		2^n \norm{\hat{q}}^n
		\norm{ \hat{p}^n }
		\\
		& \leq
		2^n 
		\norm{\hat{q}}^n
		\norm{\hat{p}}^n
	\end{align*}
	So in the end we get
	\begin{equation*}
		|\hbar|^n n! \norm{ \Unit }
		\leq
		c^n
	\end{equation*}
	for $1 \norm{\hat q} \norm{\hat p} = c \in \mathbb{R}$. This cannot be 
	fulfilled for all $n \in \mathbb{N}$ unless $\norm{ \Unit } = 0$. But 
	then, by submultiplicativity, the seminorm itself must be equal to $0$.
\end{proof}
\begin{remark}
	The so called Weyl algebra, which fulfils the properties of the 
	foregoing proposition, can be constructed from a Poisson algebra with 
	constant a Poisson tensor. On one hand, it is a fair to ask the question, 
	why this restriction of not being locally m-convex should also be apply to
	linear Poisson systems. On the other hand, there is no reason to 
	expect that things become easier when we make the Poisson structure more 
	complex. Moreover, the Weyl algebra is actually nothing but a 
	quotient of the universal enveloping algebra of the so called 
	Heisenberg algebra, which is a particular Lie algebra. There is 
	no reason why the original algebra should have a ''better'' analytical 
	structure than its quotient, since the ideal, which is divided out by 
	this procedure, is a closed one.
\end{remark}
There's a second good reason why we should avoid our topology to be locally 
m-convex. The topology we set up on $\Sym^{\bullet}(\lie{g})$ for a Lie 
algebra $\lie{g}$ will also give a topology on $\mathcal{U}(\lie{g})$.
In Proposition \ref{LCAna:Prop:NoBetterTopology} ,we will show that, under 
weak (but for our purpose necessary) additional assumptions, there can be no 
topology on $\mathcal{U}(\lie{g})$, which allows an entire holomorphic 
calculus. This underlines the results from Proposition 
\ref{Prop:LCAna:QMnotLMC}, since locally m-convex algebras always have such a 
calculus.


In this sense, we have good reasons to think that 
$\Sym^{\bullet}(\lie{g})$ will not allow a better setting than the
one of a locally convex algebra if we want the Gutt star product to 
be continuous. Before we go to this task, we have to recall some
technology from locally convex analysis.



\section{Locally convex algebras}
\label{sec:chap5_LCAlg}

\subsection{Locally convex spaces and algebras}

Every locally convex algebra is also a locally convex space which 
is, of course, a topological vector space. To make clear what we talk about, 
we first give a definition which is taken from 
\cite[Definition 1.6]{rudin:1991a}.
\begin{definition}[Topological vector space]
	\label{Def:TVSpace}
	Let $V$ be a vector space endowed with a topology $\tau$. Then we call 
	$(V, \tau)$ (or just $V$, if there is no confusion possible) 
	a topological vector space, if the two following things  hold:
	\begin{definitionlist}
		\item
		for every point in $x \in V$ the set $\{x\} $ is closed and
		
		\item
		the vector space operations (addition, scalar multiplication) are 
		continuous.
	\end{definitionlist}
\end{definition}
Not all books require axiom $(i)$ for a topological vector space. It is, 
however, useful, since it assures that our topological vector 
space is Hausdorff -- a feature which we will always want to have. The proof 
for this is not difficult, but since we do not want to go too much into details 
here, we refer to \cite{rudin:1991a} again, where it can be found in the 
theorem 1.10 and 1.12.


The most important class of topological vector spaces are, at least from a 
physical point of view, locally convex ones. Almost all 
interesting physical examples belong to this class: Finite-dimensional spaces, 
inner product (or pre-Hilbert) spaces, Banach spaces, Fr\'echet spaces, 
nuclear spaces and many more. There are at least two equivalent 
definitions of what is a locally convex space. While the first is more 
geometrical, the second is better suited for our analytic purpose.
\begin{theorem}
	\label{Thm:LCAna:LCSpace}
	For a topological vector space $V$, the following things are equivalent.
	\begin{theoremlist}
		\item
		$V$ has a local base $\algebra{B}$ of the topology whose members are 
		convex.
		
		\item
		The topology on $V$ is generated by a separating family of seminorms 
		$\mathcal{P}$.
	\end{theoremlist}
\end{theorem}
\begin{proof}
	This theorem is a very well-known result and can be found in standard 
	literature, such as \cite{rudin:1991a} again, where it is divided into 
	two 	Theorems (namely 1.36 and 1.37).
\end{proof}
\begin{definition}[Locally convex space]
	\label{Def:LCSpace}
	A locally convex space is a topological vector space in which one (and 
	thus all) of the properties from Theorem \ref{Thm:LCAna:LCSpace} are 
	fulfilled.
\end{definition}
The first property explains the term ''locally convex''. 
For our concrete computations, the second property is more helpful, 
since in this setting proving continuity just means putting estimates on 
seminorms. For this purpose, one often extends the set of seminorms 
$\mathcal{P}$ to the set of all continuous seminorms $\algebra{P}$ which 
contains all seminorms that are compatible with the topology:
\begin{equation*}
	p \in \algebra{P}
	\Longleftrightarrow
	\exists_{n \in \mathbb{N}}
	\exists_{c_1, \ldots, c_n > 0}
	\exists_{p_1, \ldots, p_n \in \mathcal{P}}
	\colon
	p 
	\leq 
	\sum\limits_{i = 1}^n
	c_i p_i.
\end{equation*}
In particular, one can take maxima of finitely many continuous seminorms to get 
again a continuous seminorm. From here, we can start looking at locally convex 
algebras.
\begin{definition}[Locally convex algebra]
	\label{Def:LCAlgebra}
	A locally convex algebra is a locally convex vector space with an 
	additional algebra structure which is continuous.
\end{definition}
More precisely, let $\algebra{A}$ be a locally convex algebra and 
$\algebra{P}$ the set of all continuous seminorms, then for all $p \in 
\algebra{P}$ there exists a $q \in \algebra{P}$ such that for all $x, y \in 
\algebra{A}$ one has
\begin{equation}
	\label{LCAna:ProductContinuity}
	p(a \cdot b)
	\leq
	q(a) q(b).
\end{equation}
Remind that we did not require our algebras to be associative. The product in 
this equation could also be a Lie bracket. If we talk about associative 
algebras, we will always say it explicitly.



\subsection{A special class of locally convex algebras}

For our study of the Gutt star product, the usual continuity estimate 
\eqref{LCAna:ProductContinuity} will not be enough, since 
there will be an arbitrarily high number of nested brackets to control. 
We will need an estimate which does not depend on the number of Lie 
brackets involved. Since Lie algebras are just one type of algebras, 
we can define the property we need also for other locally convex algebras. 
\begin{definition}[Asymptotic estimate algebra]
    \label{Def:AE}
    Let $\algebra{A}$ be a locally convex algebra (not necessarily associative) 
    with $\cdot$ denoting the multiplication and $\algebra{P}$ the set 
    of all continuous seminorms. Let $p \in \algebra{P}$.
    \begin{definitionlist}
    \item \label{item:AsymptoticEstimate} 
        We call $q \in \algebra{P}$ an asymptotic estimate for $p$, if
        \begin{equation}
            \label{LCAna:AEProperty}
            p\left(
                w_n(x_1, \ldots, x_n)
            \right)
            \leq
            q(x_1) \cdots q(x_n)
        \end{equation}
        for all words $w_n(x_1, \ldots, x_n)$ made out of $n-1$
        products of the elements $x_1, \ldots, x_n \in \algebra{A}$
        with arbitrary position of placing brackets.
    \item \label{item:AEAlgebra} 
        A locally convex algebra is said to be an asymptotic estimate algebra 
        (AE algebra), if every $p \in \algebra{P}$ has an asymptotic estimate.
    \end{definitionlist}
\end{definition}
\begin{remark}[The notion ''asymptotic estimate'']
	\label{LCAna:Rem:AE1}
	\mbox{}
	\begin{remarklist}
		\item
		The term asymptotic estimate has, to the best of our knowledge, 
		first been used by Boseck, Czichowski and Rudolph in 
		\cite{boseck.czichowski.rudolph:1981a}. They gave a seemingly weaker
		definition of asymptotic estimates, which is in fact equivalent.
		They wanted that for every seminorm $p\in \algebra{P}$, there is a 
		$m \in \mathbb{N}$ and a $q \in \algebra{P}$ such that for all 
		$n \geq m$ one has
		\begin{equation}
			\label{LCAna:PseudiAE}
			p \left( x_1 \cdots x_n \right)
			\leq
			q \left(x_1\right) \cdots q \left(x_n\right)
			\quad
			\forall_{x_1, \ldots, x_n \in \algebra{A}}.
		\end{equation}
		But here we can set $m = 1$, since we just need to take the maximum of 
		a finite number of continuous seminorms. Let $q$ satisfy 
		\eqref{LCAna:PseudiAE}. By Continuity, we have for all 
		$i = 2, \ldots, m-1$
		\begin{equation*}
		 	p(x_1 \cdots x_i)
		 	\leq
		 	q^{(i)}(x_1) \ldots q^{(i)}(x_i)
		 	\quad
		 	\forall_{x_1, \ldots, x_i \in \algebra{A}}
		\end{equation*}
		Now we get an asymptotic estimate $q'$ for $p$ in our sense by setting
		\begin{equation*}
		 	q'
		 	=
		 	\max\{ 
		 		p, q^{(2)}, \ldots, q^{(m-1)}, q
		 	\}.
		\end{equation*}
		Also AE algebras were defined by Boseck et al. in 
		\cite{boseck.czichowski.rudolph:1981a}, but here the notion is really 
		different from ours: for them, in an AE algebra every continuous 
		seminorm admits a sequence of asymptotic estimates. This sequence must 
		fulfil two additional properties, which actually make the algebra 
		locally 	m-convex. Our definition is weaker,	since it does not imply, 
		a priori, the existence of an topologically equivalent set of 
		submultiplicative seminorms.
		
		\item
		In \cite{gloeckner.neeb:2012a}, Gl\"ockner and Neeb used a property to 
		which they referred as $(*)$ for associative algebras. It was then 
		used in 	\cite{bogfjellmo.dahmen.schmedig:2015a} by Bogfjellmo, Dahmen 
		and Schmedig, who called it the $GN$-property. It is rather easy to 
		see that it is equivalent to our AE condition. 
	\end{remarklist}
\end{remark}

There are, of course, a lot of examples of AE (Lie) algebras. 
All finite dimensional and Banach (Lie) algebras fulfil Inequality
\eqref{LCAna:AEProperty}, just as locally m-convex (Lie) algebras do. 
The same is true for nilpotent locally convex Lie algebras, 
since here again one just has to take the maximum of a finite 
number of semi-norms, analogously to the procedure in Remark 
\ref{LCAna:Rem:AE1}. On the other hand, it is not clear what the AE property 
implies exactly. Are there examples for associative algebras which are AE but 
not locally m-convex, for example? Are there Lie algebras which are truly AE 
and not locally m-convex or nilpotent? We don't have an answer to this 
questions, but we can make some simple observations, which allow us to give an 
answer for special cases.
\begin{proposition}[Entire calculus]
	Let $\mathcal{A}$ be an associative AE algebra. Then it admits an
	entire calculus.
\end{proposition}
\begin{proof}
	The proof is the same as for locally m-convex algebras: let 
	$f \colon \mathbb{C} \longrightarrow \mathbb{C}$ be an entire 
	function with $f(z) = \sum_{n=0}^{\infty} a_n z^n$ and $p$
	a continuous seminorm with an asymptotic estimate $q$.
	Then one has $\forall_{x \in \mathcal{A}}$
	\begin{equation*}
		p(f(x))
		=
		p \left(
			\sum\limits_{n=0}^{\infty}
			a_n x^n
		\right)
		\leq
		\sum\limits_{n=0}^{\infty}
		|a_n| 
		p \left( x^n \right)
		\leq
		\sum\limits_{n=0}^{\infty}
		|a_n| q(x)^n
		<
		\infty.
	\end{equation*}
\end{proof}
\begin{remark}[Entire Calculus, AE and LMC algebras]
	The fact that associative AE algebras have an entire calculus makes them 
	very similar to locally m-convex ones.
	Now there is something we can say about associative algebras which have an 
	entire calculus: if such an algebra is additionally commutative and 
	Fr\'echet, then must be even locally m-convex. This statement was proven 
	in \cite{mitiagin.rolewicz.zelazko:1962a} by Mitiagin, Rolewicz and 
	{\.Z}elazko. Oudadess and El kinani extended this result to commutative, 
	associative algebras, in which the Baire category theorem holds 
	\cite{elkinani.oudadess:1997a}. For non-commutative algebras, the 
	situation is different. There are associative ''Baire algebras'' having an 
	entire calculus, which are not locally m-convex. {\.Z}elazko gave an 
	example for such an algebra in \cite{zelazko:1994a}. Unfortunately, his 
	example is also not AE. It seems to be is an interesting (and non-trivial) 
	question, if a non locally m-convex but AE algebra exists at all and if 
	yes, how an example could look like.
\end{remark}



\subsection{The projective tensor product}

We want to set up a topology on $\Sym^{\bullet}(\lie{g})$. Therefore, 
we will first construct a topology on the tensor algebra $\Tensor^{\bullet}
(\lie{g})$. Since the construction is possible starting from any locally 
convex vector space, we want to go back to this more general setting for a 
moment. $V$ will always denote a locally convex vector space and $\algebra{P}$ 
the set of its continuous seminorms. In this situation, we can use the 
projective tensor product $\tensor[\pi]$ to get a locally convex 
topology on each tensor power $V^{\tensor[\pi] n}$. The precise construction 
of the projective tensor product can be found in good textbooks on locally 
convex analysis like \cite[Chapter 15]{jarchow:1981a} or in the lecture notes 
\cite[Lemma 4.1.4]{waldmann:2014a:script}. 
Recall that for $p_1, \ldots, p_n \in \algebra{P}$ we have a continuous 
seminorm on $V^{\tensor[\pi] n}$ via
\begin{equation*}
	(p_1 \tensor[\pi] \cdots \tensor[\pi] p_n)(x)
	=
	\inf
	\left\{
	\left.
		\sum_i
		p_1 \left( x_i^{(1)} \right)
		\cdots
		p_n \left( x_i^{(n)} \right)
	\ \right| \
		x
		=
		\sum_i
		x_i^{(1)}
		\tensor \cdots \tensor
		x_i^{(n)}
	\right\}.
\end{equation*}
On factorizing tensors, we moreover have the property
\begin{equation}
	\label{LCAna:FactorTensor}
	(p_1 \tensor[\pi] \cdots \tensor[\pi] p_n)
	(x_1 \tensor[\pi] \cdots \tensor[\pi] x_n)
	=
	p_1(x_1) \cdots p_n(x_n)
\end{equation}
which will be extremely useful in the following and which can be proven by
the Hahn-Banach theorem. We also have 
\begin{equation*}
	(p_1 \tensor \cdots \tensor p_n) 
	\tensor 
	(q_1 \tensor \cdots \tensor q_m) 
	= 
	p_1 \tensor \cdots \tensor p_n \tensor q_1 \tensor \cdots \tensor q_m.
\end{equation*}
For a given $p \in \algebra{P}$ we will denote $p^n = p^{\tensor[\pi] n}$ and 
$p^0$ is just the absolute value on the field $\mathbb{K}$. The $\pi$-topology 
on $V^{\tensor[\pi] n}$ is set up by all the projective tensor products of 
continuous seminorms, or, equivalently, by all the $p^n$ for $p \in 
\algebra{P}$.

The projective tensor product has a very helpful feature: if we want to show a 
(continuity) estimate on the tensor algebra, it is enough to do so on 
factorizing tensors. We will use this very often and just refer to it as the 
''infimum argument''.
\begin{lemma}[Infimum argument for the projective tensor product]
	\label{LCAna:Lemma:InfimumArgument}
 	Let $V_1, \ldots, V_n$, \hfill  \\
 	$W$ be locally convex vector spaces and 
	\begin{equation*}
		\phi \colon
		V_1 \times \cdots \times V_n
		\longrightarrow
		W
	\end{equation*}
	a $n$-linear map, from which we get the linear map 
	$\Phi \colon V_1 \tensor[\pi] \cdots \tensor[\pi] V_n \longrightarrow W$.
	Then $\Phi$ is continuous if and only if this is true for $\phi$. 
	If the estimate
	\begin{equation}
		\label{LCAna:ContOnFactors}
		p \left(
			\Phi (x_1 \tensor \cdots \tensor x_n)
		\right)
		\leq
		q_i(x_1) \cdots q_i(x_n)
	\end{equation}
	is fulfilled for $p\in\algebra{P}_V$ and $q_i \in \algebra{P}_{W_i}$ 
	and all $x_i \in V_i, i=1, \ldots, n$ then we have
	\begin{equation}
		\label{LCAna:ContGeneral}
		p \left(
			\Phi (x)
		\right)
		\leq
		\left( q_1 \tensor \cdots \tensor q_n \right)(x)
	\end{equation}
	for all $x \in V_1 \tensor \cdots \tensor V_n$.
\end{lemma}
\begin{proof}
	If $\Phi$ is continuous, the continuity of $\phi$ is clear. 
	The other implication is more interesting.
	Continuity for $\phi$ means, that for every continuous seminorm $p$ on 
	$W$ we have continuous seminorms $q_i$ on $V_i$ with $i = 1, \ldots, n$ 
	such that for all $x^{(i)} \in V_i$ the estimate
	\begin{equation}
		\label{LCAna:ContiFactorTensors}
		p \left(
			\phi\left( x^{(1)}, \ldots, x^{(n)} \right)
		\right)
		\leq
		q_1 \left( x^{(1)} \right) 
		\cdots 
		q_n \left( x^{(n)} \right)
	\end{equation}
	holds. Let $x \in V_1 \tensor[\pi] \ldots \tensor[\pi] V_n$, then it 
	has a representation in terms of factorizing tensors like
	\begin{equation*}
		x
		=
		\sum_j
		x_j^{(1)} 
		\tensor[\pi] \cdots \tensor[\pi] 
		x_j^{(n)}.
	\end{equation*}
	We thus have
	\begin{align*}
		p( \Phi(x) )
		& =
		p \left(
			\sum_j
			\Phi \left(
				x_j^{(1)} 
				\tensor[\pi] \cdots \tensor[\pi] 
				x_j^{(n)}
			\right)
		\right)
		\\
		& \leq
		\sum_j
		p \left(
			\phi \left(
				x_j^{(1)} 
				, \cdots ,
				x_j^{(n)}
			\right)
		\right)
		\\
		& \leq
		\sum_j
		q_1 \left( x_j^{(1)} \right) 
		\cdots 
		q_n \left( x_j^{(n)} \right).
	\end{align*}
	Now we take the infimum over all possibilities of writing $x$ as a sum of 
	factorizing tensors on both sides. While nothing will happen on the left 
	hand side, on the right hand side we will find $\left( q_1 \tensor[\pi] 
	\ldots \tensor[\pi] q_n \right)(x)$: 
	\begin{equation*}
		p( \Phi(x) )
		\leq
		\inf
		\left\{
		\left.
			\sum_j
			q_1 \left( x_j^{(1)} \right) 
			\cdots 
			q_n \left( x_j^{(n)} \right)
		\ \right| \
			x
			=
			\sum_j
			x_j^{(1)} \cdots x_j^{(n)}
		\right\}.
	\end{equation*}
	This is the estimate we wanted and the Lemma is proven.
\end{proof}


Most of the time, we will deal with the symmetric tensor algebra. Therefore, 
we want to recall some basic facts about $\Sym^n(V)$, when it inherits the 
$\pi$-topology from the $V^{\tensor[\pi] n}$. We will call it 
$\Sym_{\pi}^n(V)$ when we endow it with this topology.
\begin{lemma}
	\label{Lemma:LCAna:ProjTensSymm}
	Let $V$ be a locally convex vector space, $p$ a continuous seminorm 
	and $n,m \in \mathbb{N}$.
	\begin{lemmalist}
		\item
		The symmetrization map
		\begin{equation*}
			\Symmetrizer_n
			\colon
			V^{\tensor_{\pi} n}
			\longrightarrow
			V^{\tensor_{\pi} n}
			, \quad
			(x_1 \tensor \ldots \tensor x_n)
			\longmapsto
			\frac{1}{n!}
			\sum\limits_{\sigma \in S_n}
			x_{\sigma(1)}
			\tensor \ldots \tensor
			x_{\sigma(n)}
		\end{equation*}
		is continuous and we have for all $x \in V^{\tensor_{\pi} n}$ 
		the estimate
		\begin{equation}
			\label{LCAna:SymmProdCont}
			p^n(\Symmetrizer_n(x))
			\leq
			p^n(x).
		\end{equation}
		
		\item
		Each symmetric tensor power $\Sym_{\pi}^n(V) \subseteq 
		V^{\tensor_{\pi} n}$ is a closed subspace.
		
		\item
		For $x \in \Sym_{\pi}^n(V)$ and $y \in \Sym_{\pi}^m(V)$ we have
		\begin{equation*}
			p^{n + m}(xy)
			\leq
			p^n(x) p^m(y).
		\end{equation*}
	\end{lemmalist}
\end{lemma}
\begin{proof}
	The first part is very easy to see and uses most of the tools which are 
	typical for the projective tensor product. We have the estimate for 
	factorizing tensors $x_1 \tensor \ldots \tensor x_n$
	\begin{align*}
		p^n \left(
			\Symmetrizer \left(
				x_1 \tensor \ldots \tensor x_n
			\right)
		\right)
		& =
		p^n \left(
			\frac{1}{n!}
			\sum	\limits_{\sigma \in S_n}
			x_{\sigma(1)} 
			\tensor \ldots \tensor 
			x_{\sigma(n)}
		\right)
		\\
		& \leq
		\frac{1}{n!}
		\sum\limits_{\sigma \in S_n}
		p^n \left(
			x_{\sigma(1)} 
			\tensor \ldots \tensor 
			x_{\sigma(n)}
		\right)
		\\
		& =
		\frac{1}{n!}
		\sum\limits_{\sigma \in S_n}
		p \left( x_{\sigma(1)} \right)
		\ldots
		p \left( x_{\sigma(n)} \right)
		\\
		& =
		p \left( x_1 \right)
		\ldots
		p \left( x_n \right)
		\\
		& =
		p^n \left(
			x_1 \tensor \ldots \tensor x_n
		\right).
	\end{align*}
	Then we use the infimum argument from Lemma 
	\ref{LCAna:Lemma:InfimumArgument} and we are done.
	The second part is also easy since the kernel of a continuous map is
	always a closed subspace of the initial space and we have
	\begin{equation*}
		\Sym_{\pi}^n 
		= 
		\ker (\id - \Symmetrizer_n).
	\end{equation*}
	The third part is a consequence from the first.
\end{proof}
One could maybe think that the inequality in the first part of this lemma is 
just an artefact which is due to the infimum argument and should actually be 
an equality, if one looked at it more closely. It is very interesting to see, 
that this is \textit{not} the case, since it may happen that this 
inequality is strict. The following example illustrates this.
\begin{example}
	We take $V = \mathbb{R}^2$ with the standard basis $e_1,	e_2$ 
	and $V$ is endowed with the maximum norm. Hence we have $\norm{e_1} = 
	\norm{e_2} = 1$. Now look at $e_1 \tensor e_2$, which has the norm
	\begin{equation*}
		\norm{
			e_1 \tensor e_2
		}
		= 
		\norm{e_1}
		\tensor
		\norm{e_2}
		=
		1
	\end{equation*}
	We now evaluate the symmetrization map on $V \tensor[\pi] V$:
	\begin{equation*}
		\Symmetrizer \left(
			e_1 \tensor e_2
		\right)
		=
		\frac{1}{2}
		\left(
			e_1 \tensor e_2
			+
			e_2 \tensor e_1
		\right).
	\end{equation*}
	Our aim is to show, that the projective tensor product of the norm of this 
	symmetrized vector is not $1$. Therefore we need to find another way of 
	writing it which has a norm of less than $1$. Observe that
	\begin{equation*}
		\frac{1}{2}
		(e_1 \tensor e_2 + e_2 \tensor e_1)
		=
		\frac{1}{4}
		(
			(e_1 + e_2) \tensor (e_1 + e_2)
			+
			(-e_1 + e_2) \tensor (e_1 - e_2)
		)
	\end{equation*}
	and we have
	\begin{align*}
		& 
		\frac{1}{4}
		\norm{
			(e_1 + e_2) \tensor (e_1 + e_2)
			+
			(-e_1 + e_2) \tensor (e_1 - e_2)
		}
		\\
		& \leq
		\frac{1}{4}
		(
			\norm{ (e_1 + e_2) \tensor (e_1 + e_2) }
			+
			\norm{ (-e_1 + e_2) \tensor (e_1 - e_2) }
		)
		\\
		& \leq
		\frac{1}{4}
		(
			\norm{e_1 + e_2}
			\cdot
			\norm{e_1 + e_2}
			+
			\norm{- e_1 + e_2}
			\cdot
			\norm{e_1 - e_2}
		)
		\\
		& =
		\frac{1}{4}
		(1 \cdot 1 + 1 \cdot 1)
		\\
		& =
		\frac{1}{2}.
	\end{align*}
	So we have $\norm{\Symmetrizer(e_1 \tensor e_2)} \leq \frac{1}{2} < 1$.
\end{example}


\subsection{A Topology for the Gutt Star Product}

The next step is to set up a topology on $\Tensor^{\bullet}(V)$ which 
has the $\pi$-topology on each component. A priori, there are a lot of such 
topologies and at least two natural ones: the direct sum topology which is 
very fine and has a very small closure, and the cartesian product topology 
which is very coarse and therefore has a very big closure. We need something 
in between, which we can adjust in a convenient way.
\begin{definition}[$\Tensor_R$-topology]
	Let $p$ be a continuous seminorm on a locally convex vector space 
	$V$ and $R \in \mathbb{R}$. We define by 
	\begin{equation*}
		p_R 
		= 
		\sum\limits_{n=0}^{\infty}
		n!^R p^n
	\end{equation*}
	a seminorm on the Tensor algebra $\Tensor^{\bullet}(V)$. We write for 
	the tensor or the symmetric algebra endowed with all such seminorms  
	$\Tensor_R^{\bullet}(V)$ or $\Sym_R^{\bullet}(V)$ respectively.
\end{definition}
Now we want to collect the most important results on the locally convex 
algebras $\left( \Tensor_R^{\bullet}(V), \tensor \right)$ and $\left( 
\Sym_R^{\bullet}(V), \vee \right)$. 
\begin{lemma}[The $\Tensor_R$-topology]
    \label{Lemma:LCAna:Projections}%
    Let $R' \geq R \geq 0$ and $q, p$ are continuous semi-norms on $V$.
    \begin{lemmalist}
	  \item \label{Item:EstimateForSeminorms}
	    	If $q \geq p$ then $q_R \geq p_R$ and $p_{R'} \geq p_R$.
	  \item \label{Item:TensorProductContinuous}
	    	The tensor product is continuous and satisfies the following 
	    	inequality:
	    	 \begin{equation*}
	    		p_R(x \tensor y)
	    		\leq
	    		\left( 2^R p \right)_R(x)
	    		\left( 2^R p \right)_R(y)
	    	\end{equation*}
	  \item \label{Item:PitopologyOnComponents}
	    	For all $n \in \mathbb{N}$ the induced topology on 
	    	$\Tensor^n(V) \subset \Tensor_R^{\bullet}(V)$ and on 
	    	$\Sym^n(V) \subset \Sym_R^{\bullet}(V)$ is the $\pi$-
	    	topology.
	  \item \label{Item:ComponentProjectionsContinuous}
	    	For all $n \in \mathbb{N}$ the projection and the inclusion 
	    	maps
	        \begin{equation*}
	        	\begin{array}{ccccc}
		    	    \Tensor_R^{\bullet}(V)
		        	&
	    	   		\ot{$\pi_n$}{\longrightarrow}
	    	    		&
	    	    		V^{\tensor_{\pi} n}
	    	    		&
	    	    		\ot{$\iota_n$}{\longrightarrow}
	    		    &
	    		    \Tensor^{\bullet}(V)
	    		    \\
		        \Sym_R^{\bullet}(V)
		        &
	    	        \ot{$\pi_n$}{\longrightarrow}
	    	    		&
	    	    		\Sym_{\pi}^n(V)
	    	    		&
	    	    		\ot{$\iota_n$}{\longrightarrow}
	    		    &
	    		    \Sym_R^{\bullet}(V)
	        	\end{array}
	        \end{equation*}
	        are continuous.
	  \item \label{Item:CompletionExplicitly}
    		The completions $\widehat{\Tensor}_R^{\bullet}(V)$ of 
    		$\Tensor_R^{\bullet}(V)$ and $\widehat{\Sym}_R^{\bullet}(V)$ 
    		of $\Sym_R^{\bullet}(V)$ can be described explicitly as
    		\begin{equation*}
	    		\begin{array}{ccccc}
		    		\widehat{\Tensor}_R^{\bullet}(V)
		    		&
		    		=
		    		&
		    		\left\{
		    		\left.
		    			x
		    			=
		    			\sum\limits_{n=0}^{\infty}
		    			x_n
		    		\ \right| \ 
		    			p_R(x)
		    			<
		    			\infty
		    			, \text{ for all } p
		    		\right\}
		    		&
		    		\subseteq
		    		&
		    		\prod\limits_{n=0}^{\infty}
		    		V^{\hat{\tensor}_{\pi} n}
		    		\\
		    		\widehat{\Sym}_R^{\bullet}(V)
		    		&
		    		=
		    		&
		    		\left\{
		    		\left.
		    			x
		    			=
		    			\sum\limits_{n=0}^{\infty}
		    			x_n
		    		\ \right| \ 
		    			p_R(x)
		    			<
		    			\infty
		    			, \text{ for all } p
		    		\right\}
		    		&
		    		\subseteq
	    			&
	    			\prod\limits_{n=0}^{\infty}
	    			\Sym_{\hat{\tensor}_{\pi}}^n
	    		\end{array}
    		\end{equation*}
    		with $p$ running through all continuous semi-norms on $V$ and
    		the $p_R$ are extended to the Cartesian product allowing the 
	    	value $+ \infty$.
      \item \label{Item:StrictlyFinerForBiggerR}
    		If $R' > R$, then the topology on $\Tensor_{R'}^{\bullet}(V)$ 
    		is strictly finer than the one on $\Tensor_R^{\bullet}(V)$, 
    		the same holds for $\Sym_{R'}^{\bullet}(V)$ and 
    		$\Sym_R^{\bullet}(V)$. Therefore the completions get smaller 
    		for bigger $R$.
      \item \label{Item:ComponentInclusionsContinuous}
    		The inclusion maps $\widehat{\Tensor}_{R'}^{\bullet}(V) 
    		\longrightarrow \widehat{\Tensor}_R^{\bullet}(V)$ and 
    		$\widehat{\Sym}_{R'}^{\bullet}(\lie{g}) \longrightarrow 
    		\widehat{\Sym}_R^{\bullet}(\lie{g})$ are continuous.
	  \item \label{Item:LmcJustForZero}
    		The topology on $\Tensor_R^{\bullet}(V)$ with the tensor 
    		product and on $\Sym_R^{\bullet}(V)$ with the symmetric 
    		product is locally m-convex if and only if $R = 0$.
      \item \label{Item:FirstCountable}
    		The algebras $\Tensor_R^{\bullet}(V)$ and $\Sym_R^{\bullet}(V)$
    		are first countable if and only if this is true for $V$.
      \item \label{item:PointsArePoints} The evaluation functionals
        $\delta_{\varphi}\colon \Sym^\bullet_R(V) \longrightarrow
        \mathbb{K}$ for $\varphi \in \lie{g}'$ are continuous.
    \end{lemmalist}
\end{lemma}
\begin{proof}
	The first part is clear on factorizing tensors and extends to the whole 
	tensor algebra via the infimum argument. For part $(ii)$, take two 
	factorizing tensors
	\begin{equation*}
		x
		=
		x^{(1)} \tensor \cdots \tensor x^{(n)}
		\quad \text{ and }
		y
		=
		y^{(1)} \tensor \cdots \tensor y^{(m)}
	\end{equation*}
	and compute:
	\begin{align*}
		p_R \left(
			x \tensor y
		\right)
		& =
		(n + m)!^R
		p^{n + m} \left(
			x^{(1)} \tensor \cdots \tensor x^{(n)}
			\tensor
			y^{(1)} \tensor \cdots \tensor y^{(m)}
		\right)
		\\
		& =
		(n + m)!^R
		p^n \left(
			x^{(1)} \tensor \cdots \tensor x^{(n)}
		\right)
		p^m \left(
			y^{(1)} \tensor \cdots \tensor y^{(m)}
		\right)
		\\
		& =
		\binom{n + m}{n}^R
		n!^R m!^R
		p^n \left(
			x^{(1)} \tensor \cdots \tensor x^{(n)}
		\right)
		p^m \left(
			y^{(1)} \tensor \cdots \tensor y^{(m)}
		\right)
		\\
		& \leq
		2^{(n + m) R}
		p_R \left( x^{(1)} \tensor \cdots \tensor x^{(n)} \right)
		p_R \left( y^{(1)} \tensor \cdots \tensor y^{(m)} \right)
		\\
		& =
		\left( 2^R p\right)_R 
		\left( x^{(1)} \tensor \cdots \tensor x^{(n)} \right)
		\left( 2^R p \right)_R 
		\left( y^{(1)} \tensor \cdots \tensor y^{(m)} \right).
	\end{align*}
	The parts $(iii)$ and $(iv)$ are clear from the construction of the 
	$R$-	topology. In part $(v)$ we used the completion of the tensor product 
	$\hat{\tensor}$, the statement itself is clear and implies $(vi)$ 
	directly, since we have really more elements in the completion for $R < 
	R'$, like the series over $x^{n} \frac{1}{n!^t}$ for $t \in (R, R')$ and 
	$0 \neq x \in V$. Statement $(vii)$ follows from the first. For $(viii)$, 
	it is easy to see that $\Tensor_0^{\bullet}(V)$ and $\Sym_0^{\bullet}(V)$ 
	are locally m-convex. For every $R > 0$ we have
	\begin{equation*}
		p_R \left(x^n \right)
		=
		n!^R
		p(x)^n
	\end{equation*}
	for all $n \in \mathbb{N}$ and all $x \in V$. If we had a 
	submultiplicative seminorm $\varphi$ from an equivalent topology, 
	then we would have some $x \in V$, and a continuous seminorm $p$ with 
	$p(x) \neq 0$ such that $p_R \leq \varphi$, and hence
	\begin{equation*}
		n!^R p(x)^R
		\leq
		\varphi \left(x^n\right)
		\leq
		\varphi\left(x\right)^n.
	\end{equation*}
	Since this is valid for all $n \in \mathbb{N}$, we get a contradiction.
	For the ninth part, the tensor algebras can not be first countable if this 
	is not true for $V$ itself. On the other hand, if $V$ has a finite base of 
	the topology, then $\Tensor_R^{\bullet}(V)$ and $\Sym_R^{\bullet}(V)$ are 
	just a countable multiple of $V$ and stay therefore first countable.
	The last part finally assures, that every symmetric tensor really gives a 
	continuous function and comes from the continuity of $\varphi$.
\end{proof}
The projective tensor product obviously keeps a lot of important and 
strong properties of the original vector space $V$. But Lemma 
\ref{Lemma:LCAna:Projections} still leaves out some important things. 
We will not make use of them in the following, but it is worth naming 
them for completeness. To do this in full generality, we 
need one more definition, which will be also very important in chapter 6.
\begin{definition}\label{ProjectiveLimit}
	For a locally convex vector space $V$ and $R \geq 0$ we set
	\begin{equation*}
		\Sym_{R^-}^{\bullet}(V)
		=
		\projlim\limits_{\epsilon \longrightarrow 0}
		\Sym_{1 - \epsilon}^{\bullet}(V)
	\end{equation*}
	and call its completion $\widehat{\Sym}_{R^-}^{\bullet}(V)$.
\end{definition}
The projective limit is the intersection of all the algebras 
$\Sym_R^{\bullet}(V)$ for $R < 1$. Its completion can be understood as all 
those series in the cartesian product, which converge for all $p_R$ for $R < 1$ 
and $p$ a continuous seminorm on $V$. We hence see that the completion 
$\widehat{\Sym}_{R^-}^{\bullet}(V)$ is bigger than $\widehat{\Sym}_R^{\bullet}
(V)$ without the projective limit. This will become important in chapter 6.
Now we can state two more propositions. Since we won't use them, we omit the 
proofs here. They can be found in \cite{waldmann:2014a}.
\begin{proposition}[Schauder bases]
	\label{Prop:LCAna:Bases}
	Let $R \geq 0$ and $V$ a locally convex vector space.
	If $\{e_i\}_{i \in I}$ is an absolute Schauder basis of $V$ with 
	coefficient functionals $\{\varphi^i\}_{i \in I}$, i.e. for every 
	$x \in V$ we have
	\begin{equation*}
		x
		=
		\sum\limits_{i \in I}
		\varphi^i(x) e_i
	\end{equation*}
	such that for every $p \in \algebra{P}$ there is a 
	$q \in \algebra{P}$ such that
	\begin{equation}
		\label{LCAna:AbsoluteSchauder}
		\sum\limits_{i \in I}
		|\varphi^i(x)|
		p(e_i)
		\leq
		q(x),
	\end{equation}
	then the set 
	$\{e_{i_1} \tensor \ldots \tensor e_{i_n}\}_{i_1, \ldots, i_n \in I}$ 
	defines an absolute Schauder basis of $\Tensor_R^{\bullet}(V)$ 
	together with the linear functionals $\{\varphi^{i_1} \tensor \ldots 
	\tensor 	\varphi^{i_n}\}_{i_1, \ldots, i_n \in I}$ which satisfy
	\begin{equation*}
		\sum\limits_{n=0}^{\infty}
		\sum\limits_{i_1, \ldots, i_n \in I}
		\left| 
			\left(
				\varphi^{i_1} \tensor \ldots \tensor \varphi^{i_n}
			\right)
			(x)
		\right|
		p_R \left(
			e_{i_1} \tensor \ldots \tensor e_{i_n}
		\right)
		\leq
		q_R (x)
	\end{equation*}
	for every $x \in \Tensor_R^{\bullet}(V)$ whenever $p$ and $q$ satisfy 
	\eqref{LCAna:AbsoluteSchauder}. The same statement is true for 
	$\Sym_R^{\bullet}(V)$ and for $\Sym_{R^-}^{\bullet}(V)$ (for $R > 0$) when 
	we choose a maximal linearly independent subset out of the set $\{e_{i_1} 
	\ldots e_{i_n}\}_{i_1, \ldots, i_n \in I}$.
\end{proposition}
\begin{proposition}[Nuclearity]
	\label{LCAna:Nuclearity}
	Let $V$ be a locally convex space. For $R \geq 0$ the following statements 
	are equivalent:
	\begin{propositionlist}
	  \item
		$V$ is nuclear.
	  \item
	  	$\Tensor_R^{\bullet}(V)$ is nuclear.
	  \item
	  	$\Sym_R^{\bullet}(V)$ is nuclear.	  	
	\end{propositionlist}
	If moreover $R > 0$, then the following statements are equivalent:
	\begin{propositionlist}
	  \item
		$V$ is strongly nuclear.
	  \item
	  	$\Tensor_R^{\bullet}(V)$ is strongly nuclear.
	  \item
	  	$\Sym_R^{\bullet}(V)$ is strongly nuclear.
	\end{propositionlist}
\end{proposition}
Nuclearity is an important and natural property in physics. Actually every 
example of a locally convex vector space, which play a role in physics, is 
either a normed space or nuclear. Therefore we want this property to be 
conserved.
\begin{remark}[The $\Tensor_R$-topology in the literature]
	It seems that this topology is actually not a new construction, but it 
	was already found and refound in the past. A very similar construction is 
	due to Goodman \cite{goodman:1971a}, who looked at finite-dimensional 
	Lie algebras. He studied differential operators on the Lie group, that 
	means the universal enveloping algebra, which he topologised via the 
	tensor algebra using basically the same weights. He needed a basis to do so 
	and proved afterwards that the topology he found is independent of the 
	choice of the basis. He also showed the continuity of the multiplication, 
	but by going a different way: he proved that certain ideals are 
	closed in this topology and divided them out. In this sense his approach 
	is less explicit than ours and also does not apply to infinite-dimensional 
	Lie algebras, where the proofs are more involved. Goodman was more 
	interested in the representation theory which arises from his construction 
	and he also knew about its functoriality. However, he did not know 
	about the deformation aspect behind it, since the ideas of deformation 
	quantization did not exist at that time. It seems a bit like his work has 
	gone more or less unnoticed, we could not find a work which used this 
	topology later for studies in Lie theory. A very different way of 
	constructing a topology which coincides with ours for $R = 1$ was moreover 
	given before by Ra{\v{s}}evski{\u{i}} in \cite{rasevskii:1966a}, who also 
	restricted to the finite-dimensional case and used bases of his Lie algebra 
	to construct the topology. For this reason, also his ideas are bounded to 
	finite-dimensional Lie algebras.
\end{remark}



\section{Continuity results for the Gutt star product}
\label{sec:chap5_TopologyStar}

From now on, we start with an AE Lie algebra $\lie{g}$ rather than with a 
general locally convex space $V$. We have most of the tools at hand to show the 
continuity of the Gutt star product, except for precise estimates on the 
$\bchtilde{a}{b}{\xi}{\eta}$-terms. Therefore, we state the following lemma.
\begin{lemma}
	\label{LCAna:Lemma:BCHTermsEstiamte}
	Let $\lie{g}$ be a AE-Lie algebra, $\xi, \eta \in \lie{g}$, $p$ a 
	continuous seminorm, $q$ an	asymptotic estimate for it and $a, b, n \in 
	\mathbb{N}$ with $a + b = n$. Then, using the Goldberg-Thompson form of 
	the Baker-Campbell-Hausdorff series, we have the following estimates:
	\begin{lemmalist}
	  \item \label{Item:ThompsonEstimate}
		The coefficients $g_w$ from \eqref{Alg:BCHinGoldbergThompson} 
		fulfil the estimate
		\begin{equation}
			\label{LCAna:ThompsonEstimate}
			\sum\limits_{|w| = n}
			\left| \frac{g_w}{n} \right|
			\leq
			\frac{2}{n}.
		\end{equation}
		Recall that $|w|$ denotes the length of a word $w$ and $[w]$ is the
		word put in Lie brackets nested to  the left.
	\item \label{Item:AEonWords}
		For every word $w$, which consists of $a$ $\xi$'s and $b$ $\eta$'s,
		we have
		\begin{equation}
		\label{LCAna:AEonWords}
			p([w])
			\leq
			q(\xi)^a q(\eta)^b.
		\end{equation}
	\item \label{Item:BCHEstimate}
		We have the estimate
		\begin{equation}
		\label{LCAna:BCHEstimate}
			p \left(
				\bchtilde{a}{b}
				{\xi_1, \ldots, \xi_a}
				{\eta_1, \ldots, \eta_b}
			\right)
			\leq
			\frac{2}{a + b}
			q\left( \xi_1 \right) \cdots q\left( \xi_a \right)
			q\left( \eta_1 \right) \cdots q\left( \eta_b \right)
		\end{equation}
	\end{lemmalist}
\end{lemma}
\begin{proof}
	We already showed part $(i)$ in Proposition 
	\ref{Alg:Prop:ThompsonsEstimate} and put in the factor $\frac{1}{n}$ 
	because these factors will appear later. The next estimate 
	\eqref{LCAna:AEonWords} is due to the AE property which does not see the 
	way how brackets are set but just counts the number of $\xi_i$'s and 
	$\eta_j$'s in the whole expression.
	Let us use the notation $|w|_{\xi}$ for the number of $\xi$'s appearing
	in a word $w$ and $|w|_{\eta}$ for the number of $\eta$'s. Clearly, $|w| =
	|w|_{\xi} + |w|_{\eta}$. With \eqref{LCAna:ThompsonEstimate} and the AE
	property of $\lie{g}$, we get
	\begin{align*}
		p \left(
			\bchtilde{a}{b}
			{\xi_1, \ldots, \xi_a}
			{\eta_1, \ldots, \eta_b}
		\right)
		& \leq
		\sum\limits_{\substack{
			|w|_{\xi} = a \\
			|w|_{\eta} = b
		}}
		p^{a + b} \left(
			\frac{g_w}{a + b}
			[w]
		\right)
		\\
		& \leq
		\sum\limits_{\substack{
			|w|_{\xi} = a \\
			|w|_{\eta} = b
		}}
		\frac{ |g_w| }{a + b}
		p([w])
		\\
		& \leq
		\sum\limits_{ |w| = a + b }
		\frac{ |g_w| }{a + b}
		q\left( \xi_1 \right) \cdots q\left( \xi_a \right)
		q\left( \eta_1 \right) \cdots q\left( \eta_b \right)
		\\
		& \leq
		\frac{2}{a + b}
		q\left( \xi_1 \right) \cdots q\left( \xi_a \right)
		q\left( \eta_1 \right) \cdots q\left( \eta_b \right).
	\end{align*}
\end{proof}
For showing the continuity of the star product we can either proceed via the 
big formula \eqref{Formulas:2MonomialsFormula2} for two monomials or via the 
smaller one \eqref{Formulas:LinearMonomial2} for a monomial with a vector and 
iterate it. While the results are a bit better for the first approach, the 
second makes the proof easier. Nevertheless, both approaches give strong 
results, and this is why we will to give both proofs here.


There will be a very general way how most of the proofs will work and which 
tools will be used in the following. If we want to show the continuity of a 
map $f \colon \Sym_R^{\bullet}(\lie{g}) \longrightarrow 
\Sym_R^{\bullet}(\lie{g})$, we will proceed most of the time like this:
\begin{enumerate}
	\item \label{Item:LCAna:Step1}
	First, we extend the map to the whole tensor algebra by symmetrizing 
	beforehand: $f = f \circ \Symmetrizer$. This is a real extension since the 
	symmetrization does not affect symmetric tensors. We do this here for the 
	Gutt star product
	\begin{equation*}
		\ostar_z
		\colon
		\Tensor^{\bullet}(\lie{g})
		\tensor
		\Tensor^{\bullet}(\lie{g})
		\longrightarrow
		\Tensor^{\bullet}(\lie{g})
		, \quad
		\ostar_z 
		= 
		\star_z \circ 
		\left( \Symmetrizer \tensor \right).
	\end{equation*}
	and for the $C_n$-operators analogously.

	\item \label{Item:LCAna:Step2}
	Then we start with an estimate which we prove only on 
	factorizing tensors in order to use the infimum argument 
	(Lemma \ref{LCAna:Lemma:InfimumArgument}).

	\item \label{Item:LCAna:Step3}
	During the estimation process, we find products of Lie 
	brackets. Those will be split up by the continuity of the symmetric 
	product \eqref{LCAna:SymmProdCont} from Lemma 
	\ref{Lemma:LCAna:ProjTensSymm} the AE property \eqref{LCAna:AEProperty}.
	
	\item \label{Item:LCAna:Step4}
	Finally, we rearrange the split up seminorms to the seminorm of a 
	factorizing tensor by \eqref{LCAna:FactorTensor}.
\end{enumerate}


\subsection{Continuity of the product}
In the first proof, we want to give an estimate via the formula
\begin{equation}
    \label{eq:GstarOfXisAndEtas}
    \xi_1 \cdots \xi_k \star_z \eta_1 \cdots \eta_{\ell}
    =
    \sum\limits_{n=0}^{k + \ell -1}
    z^n
    C_n (\xi_1 \cdots \xi_k, \eta_1 \cdots \eta_{\ell}).
\end{equation}
To shorten the very long expression from Equation 
\eqref{Formulas:2MonomialsFormula22}, we abbreviate the summations by
\begin{equation}
	\label{LCAna:ShorterSumsInLongProduct}
    C_n\left(
        \xi_1 \cdots \xi_k,
        \eta_1 \cdots \eta_{\ell}
    \right)
    =
    \frac{1}{r!}
    \sum\limits_{\sigma, \tau}
    \sum\limits_{a_i, b_j}
    \bchtilde{a_1}{b_1}{\xi_{\sigma(i)}}{\eta_{\tau(j)}}
    \cdots
    \bchtilde{a_r}{b_r}{\xi_{\sigma(i)}}{\eta_{\tau(j)}},
\end{equation}
meaning the summations as given in
Proposition~\ref{Formulas:Prop:2MonomialsFormula2} and 
using $r = k + \ell - n$.
\begin{theorem}[Continuity of the star product]
    \label{Thm:LCAna:Continuity1}%
    Let $\lie{g}$ be an AE-Lie algebra, $R \geq 0$, $p$ a continuous seminorm
    with an asymptotic estimate $q$ and $z \in \mathbb{C}$.
    \begin{theoremlist}
    	\item \label{item:CnOperatorEstimate}
    	For $n \in \mathbb{N}$, the operator $C_n$ is continuous and for all
    	$x, y \in \Tensor_R^{\bullet}(\lie{g})$ we have the estimate:
    	\begin{equation}
    		\label{LCAna:CnOperators}
    		p_R \left( C_n(x,y) \right)
			\leq
        	\frac{n!^{1 - R}}{2 \cdot 8^n}
        	(16 q)_R (x)
        	(16 q)_R (y)
    	\end{equation}
    	\item \label{item:LCAna:Continuity1}
    	For $R \geq 1$, the Gutt star product is continuous and for all
    	$x, y \in \Tensor_R^{\bullet}(\lie{g})$ we have the estimate:
	    \begin{equation}
	   	    \label{LCAna:Continuity1}
	        p_R(x \ostar_z y)
	        \leq
	        (c q)_R(x) (c q)_R(y)
	    \end{equation}
	    with $c = 16(|z| + 1)$. Hence, the Gutt star product is continuous and
	    the estimate \eqref{LCAna:Continuity1} holds on
	    $\widehat{\Sym}_R^\bullet(\lie{g})$ for all $z \in \mathbb{C}$
	\end{theoremlist}
\end{theorem}
\begin{proof}
    Let us use $r = k + \ell - n$ as before and recall that the
    products are taken in the symmetric algebra. Then we can use
    Equation \eqref{LCAna:ShorterSumsInLongProduct} and put estimates on it.  
    Let $p$ be a continuous seminorm and let $q$ be an asymptotic estimate
    for it. Then we get
    \begin{align*}
        p_R \big(
            C_n \big(
                \xi_1 \tensor \cdots \tensor \xi_k, &
                \eta_1 \tensor \cdots \tensor \eta_{\ell}
            \big)
        \big)
        \\
        &=
        p_R \bigg(
         	\frac{1}{r!}
			\sum\limits_{\sigma, \tau}
			\sum\limits_{a_i, b_j}
			\bchtilde{a_1}{b_1}{\xi_{\sigma(i)}}{\eta_{\tau(j)}}
			\cdots
			\bchtilde{a_r}{b_r}{\xi_{\sigma(i)}}{\eta_{\tau(j)}}
        \bigg)
        \\
        & \ot{(a)}{\leq}
        \frac{1}{r!}
        r!^R
        \sum\limits_{\sigma, \tau}
		\sum\limits_{a_i, b_j}
        p \left(
            \bchtilde{a_1}{b_1}{\xi_{\sigma(i)}}{\eta_{\tau(j)}}
        \right)
        \cdots
        p \left(
            \bchtilde{a_r}{b_r}{\xi_{\sigma(i)}}{\eta_{\tau(j)}}
        \right)
        \\
        & \ot{(b)}{\leq}
        \frac{1}{r!^{1-R}}
        \sum\limits_{\sigma, \tau}
		\sum\limits_{a_i, b_j}
		\frac{2}{a_1 + b_1}
		\ldots
		\frac{2}{a_r + b_r}
		q(\xi_1) \cdots q(\xi_k)
		q(\eta_1) \cdots q(\eta_{\ell})
        \\
        & \ot{(c)}{\leq}
		q(\xi_1) \cdots q(\xi_k)
		q(\eta_1) \cdots q(\eta_{\ell})
        2^r
        \frac{k! \ell!}{r!^{1-R}}
        \sum\limits_{a_i, b_j}
		1,
    \end{align*}
    where we just used the continuity estimate for the symmetric
    tensor product in ($a$), Lemma~\ref{LCAna:Lemma:BCHTermsEstiamte},
    \refitem{Item:BCHEstimate}, in ($b$) and $\frac{2}{a_i + b_i} \leq
    2$ in ($c$). We estimate the number of terms in the sum and get
    \begin{equation*}
        \sum\limits_{\substack{a_1, b_1, \ldots, a_r, b_r \geq 0 \\
            a_i + b_i \geq 1 \\
            a_1 + \cdots + a_r = k \\
            b_1 + \cdots + b_r = \ell
          }}
		1
		\leq
        \sum\limits_{\substack{a_1, b_1, \ldots, a_r, b_r \geq 0 \\
            a_1 + b_1 + \cdots + a_r + b_r = k + \ell
          }}
		1
		=
		\binom{k + \ell + 2r - 1}{k + \ell}
		\leq
		2^{3(k + \ell) - 2n - 1}.
    \end{equation*}
    Using this estimate, we get
    \begin{align*}
        &p_R \big(
            C_n \big(
                \xi_1 \tensor \cdots \tensor \xi_k,
                \eta_1 \tensor \cdots \tensor \eta_{\ell}
            \big)
        \big) \\
        &\quad\leq
        q(\xi_1) \cdots q(\xi_k)
		q(\eta_1) \cdots q(\eta_{\ell})
        2^{k + \ell - n}
        \frac{k! \ell!}{(k + \ell - n)!^{1-R}}
        2^{3(k + \ell) - 2n - 1}
        \\
        &\quad=
        q_R \left(
            \xi_1 \tensor \cdots \tensor \xi_k
        \right)
        q_R \left(
            \eta_1 \tensor \cdots \tensor \eta_{\ell}
        \right)
        2^{4(k + \ell) - 3n - 1}
        \left(
        	\frac{k! \ell! n!}{(k + \ell - n)! n!}
        \right)^{1-R}
        \\
        &\quad\leq
        q_R \left(
            \xi_1 \tensor \cdots \tensor \xi_k
        \right)
        q_R \left(
            \eta_1 \tensor \cdots \tensor \eta_{\ell}
        \right)
        2^{4(k + \ell) - 3n - 1}
        2^{(1 - R)(k + \ell)}
        n!^{1 - R}
        \\
        &\quad=
        \frac{n!^{1 - R}}{2 \cdot 8^n}
        (16 q)_R \left(
            \xi_1 \tensor \cdots \tensor \xi_k
        \right)
        (16 q)_R \left(
            \eta_1 \tensor \cdots \tensor \eta_{\ell}
        \right).
    \end{align*}
    The estimate \eqref{LCAna:CnOperators} is now proven on factorizing
    tensors.
    For general tensors $x,y \in \Tensor_R^{\bullet}(\lie{g})$, we use the 
    infimum argument from Lemma~\ref{LCAna:Lemma:InfimumArgument} and the 
    first part is done. For the second part, let $x$ and $y$
    be tensors of degree at most $k$ and $\ell$ respectively. We use
    \eqref{LCAna:CnOperators} in (a), the fact that $R \geq 1$ in (b) and have
    \begin{align}
	    \nonumber
	    	p_R \left(
	    	x \star_z y
	    	\right)
	    	& =
	    	p_R \left(
	    		\sum\limits_{n=0}^{l + \ell - 1}
	    		z^n C_n(x, y)
	    	\right)
	    	\\
	    \nonumber
	    	& \leq
	    	\sum\limits_{n=0}^{k + \ell - 1}
	    	p_R \left(
	    		z^n C_n(x, y)
	    	\right)
	    	\\
	    \label{LCAna:2MonomialEstimate}
	    	& \ot{(a)}{\leq}
	    	\sum\limits_{n=0}^{k + \ell - 1}
	    	\frac{|z|^n}{2 \cdot 8^n}
	    	n!^{1 - R}
	    	(16 q)_R(x)
	    	(16 q)_R(y)
	    	\\
	    \nonumber
	    	& \ot{(b)}{\leq}
	    	\frac{(|z| + 1)^{k + \ell}}{2}
	    	(16 q)_R(x)
	    	(16 q)_R(y)
	    	\sum\limits_{n = 0}^{\infty}
	    	\frac{1}{8^n}
			\\
		\nonumber
			& \leq
	    	(16(|z| + 1) q)_R(x)
	    	(16(|z| + 1) q)_R(y).
    \end{align}
    Since estimates on $\Sym_R^{\bullet}(\lie{g})$ also hold for the
    completion, the theorem is proven.
\end{proof}
\begin{remark}[Uniform continuity]
	Part $(i)$ of the theorem makes clear, why exactly continuity will 
	only hold if $R \geq 1$: the estimate in \eqref{LCAna:CnOperators} shows, 
	that all the $C_n$ are indeed continuous for any $R \geq 0$, but only 
	for $R \geq 1$ there is something like a uniform continuity. When $R$ 
	decreases, the continuity of the $C_n$ ''gets worse'' and the uniform 
	continuity finally breaks down when the threshold $R = 1$ is trespassed. 
	But we need this uniform estimate, since we will have to control the 
	operators up to an arbitrarily high order if we want to guarantee the 
	continuity of the whole star product. Continuity up to a previously fixed
	order $n$ does not suffice.
\end{remark}


Now, we want to give a second proof, which relies on 
\eqref{Formulas:LinearMonomial2}. Approaching like this, we don't account for 
the fact that we will encounter terms like $[\eta, \eta]$ which will vanish, 
but we estimate more brutally. During this procedure, we will also count the 
formal parameter $z$ more often than it is actually there. This is why we will 
have to make assumptions on $R$ and $z$ which are a bit stronger than before. 
Moreover, we will split up tensor products and put them together again various 
times, which is the reason why an AE Lie algebra will not suffice any more: we 
will need $\lie{g}$ to be locally m-convex. But if we make these assumptions, 
we get the following lemma which will finally simplify the proof.
\begin{lemma}
    \label{LCAna:Lemma:PreContinuity2}%
    Let $\lie{g}$ be a locally m-convex Lie algebra and $R \geq1$. 
    Then if $|z| < 2 \pi$ or $R >1$ there exists for $x \in
    \Tensor^{\bullet}(\lie{g})$ of degree at most $k$, $\eta \in \lie{g}$
    and each continuous submultiplicative seminorm $p$ a constant $c_{z,R}$ 
    only depending on $z$ and $R$ such that the following estimate holds:
    \begin{equation}
        \label{LCAna:PreContinuity2}
        p_R(x \ostar_z \eta)
        \leq
        c_{z,R} (k+1)^R p_R(x) q(\eta)
    \end{equation}
\end{lemma}
\begin{proof}
    We have for $\xi_1, \ldots, \xi_k, \eta \in \lie{g}$
    \begin{align*}
        p_R 
        &
        \left(
            \xi_1 \tensor
             \cdots \tensor \xi_k \ostar_z \eta
        \right)
        =
        p_R \left(
            \sum\limits_{n=0}^k
            \frac{B_n^* z^n}{n! (k-n)!}
            \sum\limits_{\sigma \in S_k}
            \xi_{\sigma(1)} \cdots \xi_{\sigma(k - n)}
            \left(
                \ad_{\xi_{\sigma(k - n + 1)}}
                \circ \cdots \circ
                \ad_{\xi_{\sigma(k)}}
            \right)
            (\eta)
        \right)
        \\
        & =
        \sum\limits_{n=0}^k
        \frac{|B_n^*| |z|^n}{n! (k - n)!}
        \sum\limits_{\sigma \in S_k}
        (k + 1 - n)!^R
        p^{k + 1 - n}
        \left(
            \xi_{\sigma(1)} \cdots \xi_{\sigma(k - n)}
            \left(
                \ad_{\xi_{\sigma(k - n + 1)}}
                \circ \cdots \circ
                \ad_{\xi_{\sigma(k)}}
            \right)
            (\eta)
        \right)
        \\
        & \leq
        (k + 1)^R
        \sum\limits_{n=0}^k
        \frac{|B_n^*| |z|^n}{n!}
        (k - n)!^{R - 1}
        k! p(\xi_1) \cdots p(\xi_k) p(\eta)
        \\
        & =
        (k + 1)^R
        \sum\limits_{n=0}^k
        \frac{|B_n^*| |z|^n}{n!^R}
        \left( \frac{(k - n)! n!}{k!} \right)^{R - 1}
        p_R \left(
         	\xi_1 \tensor \cdots \tensor \xi_k
        \right)
        p(\eta)
        \\
        & \leq
        (k + 1)^R
		p_R \left(
         	\xi_1 \tensor \cdots \tensor \xi_k
        \right)
        p(\eta)
        \sum\limits_{n=0}^k
        \frac{|B_n^*| |z|^n}{n!^R}.
    \end{align*}
    Now if $|z| < 2 \pi$ the sum can be estimated by extending it to a
    series which converges. So we get a constant $c_{z, R}$ depending
    on $R$ and on $z$ such that
    \begin{equation*}
        p_R \left(
            \xi_1
            \tensor \cdots \tensor \xi_k
            \ostar_z
            \eta
        \right)
        \leq
        (k + 1)^R c_{z, R}
		p_R \left(
         	\xi_1 \tensor \cdots \tensor \xi_k
        \right)
        p(\eta).
    \end{equation*}
    On the other hand, if $|z| \geq 2 \pi$ and $R > 1$ we can estimate
    \begin{equation*}
        p_R \left(
            \xi_1
            \tensor \cdots \tensor \xi_k
            \ostar_z
            \eta
        \right)
        \leq
        (k + 1)^R
		p_R \left(
         	\xi_1 \tensor \cdots \tensor \xi_k
        \right)
        p(\eta)
        \left(
            \sum\limits_{n=0}^k
            \frac{|B_n^*|}{n!}
        \right)
        \left(
            \sum\limits_{n=0}^k
            \frac{|z|^n}{n!^{R - 1}}
        \right).
    \end{equation*}
    Again, both series will converge and give constants depending only
    on $z$ and $R$. Hence, we have the estimate on factorizing tensors
    and can extend this to generic tensors of degree at most $k$ by using
    the infimum argument.
\end{proof}

In the following, we assume again that either $R > 1$ or $R \geq 1$
and $|z| < 2\pi$ in order the use
Lemma~\ref{LCAna:Lemma:PreContinuity2}. Now we can give a simpler proof of 
Theorem~\ref{Thm:LCAna:Continuity1} for the case of a locally m-convex 
Lie algebra:
\begin{proof}[Alternative Proof of Theorem~\ref{Thm:LCAna:Continuity1}]
    Assume that $\lie{g}$ is now even locally m-convex.  We want to
    replace $\eta$ in the foregoing lemma by an arbitrary tensor $y$
    of degree at most $\ell$. Again, we do that on factorizing tensors
    first and get
    \begin{align*}
        p_R \big(
         	\xi_1 \tensor \cdots \tensor \xi_k 
		&
         	\ostar_z 
         	\eta_1 \tensor \cdots \tensor \eta_\ell
        \big)
        =
        p_R \left(
	        \frac{1}{\ell !}
         	\sum\limits_{\tau \in S_\ell}
         	\xi_1 \tensor \cdots \tensor \xi_k 
         	\ostar_z
         	\eta_{\tau(1)} \tensor \cdots \tensor \eta_{\tau(\ell)}
        \right)
        \\
        & \leq
        \frac{1}{\ell !}
        \sum\limits_{\tau \in S_\ell}
        p_R \left(
         	\xi_1 \tensor \cdots \tensor \xi_k 
         	\ostar_z
         	\eta_{\tau(1)} \tensor \cdots \tensor \eta_{\tau(\ell)}
        \right)
        \\
        & \leq
        c_{z,R} (k + \ell)^R
        \frac{1}{\ell !}
        \sum\limits_{\tau \in S_\ell}
        p_R \left(
         	\xi_1 \tensor \cdots \tensor \xi_k 
         	\ostar_z 
         	\eta_{\tau(1)} \ostar \cdots \ostar_z \eta_{\tau(\ell - 1)}
        \right)
        p\left( \eta_{\tau(\ell)} \right)
        \\
        & \leq
        \quad \vdots
        \\
        & \leq
        c_{z,R}^{\ell} ((k + \ell) \cdots (k + 1))^R
        \frac{1}{\ell !}
        \sum\limits_{\tau \in S_\ell}
        p_R \left( \xi_1 \tensor \cdots \tensor \xi_k \right)
        p \left( \eta_{\tau(1)} \right)
        \cdots
        p \left( \eta_{\tau(\ell)} \right)
        \\
        & =
        c_{z,R}^{\ell} \left(
        \frac{(k + \ell)!}{k! \ell!}
        \right)^R
        p_R \left( \xi_1 \tensor \cdots \tensor \xi_k \right)
        p_R \left( \eta_1 \tensor \cdots \tensor \eta_\ell \right)
        \\
        & \leq
        (2^R p)_R 
        \left( \xi_1 \tensor \cdots \tensor \xi_k \right)
        (2^R c_{z,R} p)_R 
        \left( \eta_1 \tensor \cdots \tensor \eta_\ell \right).
    \end{align*}
    Once again, we extend the estimate via the infimum argument to the whole
    tensor algebra, since the estimate depends no longer on the degree
    of the tensors.
\end{proof}


Using this approach for continuity, it is easy to see that nilpotency
of the Lie algebra will change the estimate substantially: If we knew that
we will have at most $N$ brackets because $N + 1$ brackets vanish,
then the sum in the proof of Lemma \ref{LCAna:Lemma:PreContinuity2}
would end at $N$ instead of $k$ and would therefore be independent of
the degree of $x$.


In both proofs, it is easy to see that we need at least $R \geq 1$ to
get rid of the factorials which come up because of the combinatorics
of the star product. It is nevertheless interesting to see that this
result is sharp, that means the Gutt star product really fails
continuity for $R < 1$:
\begin{example}[A counter-example]
    \label{LCAna:Ex:HeisenbergAlgebra}%
    Let $0 \leq R < 1$ and $\lie{g}$ be the Heisenberg algebra in three 
    dimensions, i.e. the Lie algebra generated by the elements 
    $P$, $Q$ and $E$ with the bracket $[P,Q] = E$ and all other brackets
    vanishing. This is a very simple example for a non-abelian Lie algebra
    and if continuity of the star product fails for this one, then we
    can not expect it to hold for more complex ones. We impose on
    $\lie{g}$ the $\ell^1$-topology with the norm $n$ and $n(P) = n(Q)
    = n(E) = 1$. This will be helpful, since here we really have the equality
    \begin{equation*}
    		n^{k + \ell} \left( X^k Y^\ell \right)
    		=
    		n^k \left( X^k \right)
    		n^\ell \left( Y^\ell \right)
    \end{equation*}
    for the symmetric product of vectors $X, Y$. Then we consider 
    the sequences
    \begin{equation*}
        a_k
        =
        \frac{P^k}{k!^{R + \epsilon}}
        \quad
        \textrm{and}
        \quad
        b_k
        =
        \frac{Q^k}{k!^{R + \epsilon}}
    \end{equation*}
    with $2 \epsilon < 1 - R$. It is easy to see that
    \begin{equation*}
        n_R(a_k)
        =
        n_R(b_k)
        =
        k!^{- \epsilon}
    \end{equation*}
    and hence we get the limit for any $c > 0$ by
    \begin{equation*}
     	\lim_{n \longrightarrow \infty}
     	(cn)_R(a_k)
     	=
     	\lim_{n \longrightarrow \infty}
     	(cn)_R(a_k)
     	=
     	0
    \end{equation*}
    We want to show that there is no $c > 0$ such that
    \begin{equation*}
        n_R(a_k \star_z b_k)
        \leq
        (c n)_R(a_k) (c n)_R(b_k).
    \end{equation*}
    In other words, $n_R(a_k \star_z b_k)$ grows faster than
    exponentially. But this is the case, since we can calculate the star
    product explicitly and see
    \begin{align*}
        n_R(a_k \star_z b_k)
        & =
        n_R \left(
        \sum\limits_{j=0}^k
        \binom{k}{j}
        \binom{k}{j}
        j! \frac{1}{k!^{2R + 2 \epsilon}}
        P^{k-j} Q^{k-j} E^j
        \right)
        \\
        & =
        \sum\limits_{j=0}^k
        \frac{k!^2 j! (2k - j)!^R}
        {(k-j)!^2 j!^2 k!^{2R + 2 \epsilon}}
        \underbrace{
        n^{2k-j}
        ( P^{k-j} Q^{k-j} E^j )
        }_{= 1}
        \\
        & =
        \sum\limits_{j=0}^k
        \underbrace{
        \binom{k}{j}^2 \binom{2k}{k} \binom{2k}{j}^{-1}
        }_{\geq 1}
        \frac{j!^{1-R}}{k!^{2 \epsilon}}
        \\
        & \geq
        \sum\limits_{j=0}^k
        \frac{j!^{1-R}}{k!^{2 \epsilon}}
        \\
        & \geq
        k!^{1 - R - 2\epsilon}.
    \end{align*}
    Finally, we get a contradiction to the continuity of the star product 
    since $a_k \star_z b_k$ is unbounded in the topology of $\Sym_R(\lie{g})$ 
    although the sequences themselves go to zero.
\end{example}



\subsection{Dependence on the formal parameter}

Now we want to analyse the completion $\widehat{\Sym}_R^{\bullet}(\lie{g})$ of
the symmetric algebra with $\star_z$. Concerning exponential functions, we 
get the following negative result:
\begin{proposition}
    \label{proposition:NoExponentialsSorry}%
    Let $\xi \in \lie{g}$ and $R \geq 1$, then $\exp(\xi) \not\in
    \widehat{\Sym}_R^{\bullet}(\lie{g})$, where $\exp(\xi) =
    \sum_{n=0}^{\infty} \frac{\xi^n}{n!}$.
\end{proposition}
\begin{proof}
    Take a seminorm $p$ such that $1 \geq p(\xi) \neq 0$. Then set 
    $c = p(\xi)^{-1} \geq 1$. For $\xi^n$ the powers in the sense of either 
    the usual tensor product, or the symmetric product or the star product
    are the same. So we have for $N \in \mathbb{N}$
    \begin{equation*}
        (cp)_R \left(
        \sum\limits_{n=0}^N
        \frac{1}{n!} \xi^n
        \right)
        =
        \sum\limits_{n=0}^N
        \frac{n!^R}{n!}
        c^n
        p(\xi)^{n}
        =
        \sum\limits_{n=0}^N
        n!^{R - 1}
        \geq
        N,
    \end{equation*}
    and hence $\exp(\xi)$ does not converge for the seminorm $(cp)_R$.
\end{proof}
When we go back to Theorem~\ref{Thm:LCAna:Continuity1}, we see that we have 
actually proven slightly more than we stated: We showed that the star product 
converges absolutely and locally uniform in $z$. This means that the star 
product is not only continuous, but also that the formal series converges 
to the star product in the completion. We can take a closer look at this proof 
in order to get a new result for the dependence on the formal parameter $z$:
\begin{proposition}[Dependence on $z$]
    \label{corollary:HolomorphicDependence}%
    Let $R \geq 1$, then for all $x, y \in \widehat{\Sym}_R^\bullet(\lie{g})$ 
    the map
    \begin{equation}
        \label{LCAna:Holomorphicity}
        \mathbb{K} \ni z
        \longmapsto
        x \star_z y \in
        \widehat{\Sym}_R^\bullet(\lie{g})
    \end{equation}
    is analytic with (absolutely convergent) Taylor expansion at $z = 0$ 
    given by Equation~\eqref{Formulas:2MonomialsFormula1}. For 
    $\mathbb{K} = \mathbb{C}$, the collection of algebras $\left\{ \left( 
    \widehat{\Sym}_R^\bullet(\lie{g}), \star_z \right) \right\}_{z \in 
    \mathbb{C}}$ is an entire holomorphic deformation of the completed 
    symmetric tensor algebra $\left( \widehat{\Sym}_R^\bullet(\lie{g}), \vee 
    \right)$.
\end{proposition}
\begin{proof}
	The crucial point is that for $x, y \in \widehat{\Sym}_R^\bullet
	(\lie{g})$ and every continuous seminorm $p$ we have an asymptotic
	estimate $q$ such that
	\begin{align*}
		p_R \left( x \star_z y \right)
		& =
		p_R
		\left(
			\sum\limits_{n=0}^{\infty}
			z^n C_n(x,y)
		\right)
		\\
		& =
		\sum\limits_{n=0}^{\infty}
		|z|^n
		p_R( C_n(x, y) )
		\\
		& \leq
		(16 q)_R (x)
        (16 q)_R (y)
		\sum\limits_{n=0}^{\infty}
        \frac{|z|^n n!^{1 - R}}{2 \cdot 8^n},
	\end{align*}
	where we used the fact that the estimate \eqref{LCAna:CnOperators}
	extends to the completion. For $R > 1$, this map is clearly analytic
	and absolutely convergent for all $z \in \mathbb{K}$.
	If $R = 1$, then for every $M \geq 1$ we go back to homogeneous,
	factorizing tensors $x^{(k)}$ and $y^{(\ell)}$ of degree $k$ and $\ell$
	respectively, and have
	\begin{align*}
		M^{n} p_R \left(
			C_n \left( x^{(k)}, y^{(\ell)} \right)
		\right)
		& \leq
		\frac{M^n}{2 \cdot 8^n}
		(16 q)_R \left( x^{(k)} \right)
		(16 q)_R \left( y^{(\ell)} \right)
		\\
		& \leq
		M^{k + \ell}
		(16 q)_R \left( x^{(k)} \right)
		(16 q)_R \left( y^{(\ell)} \right)
		\\
		& =
		(16M q)_R \left( x^{(k)} \right)
		(16M q)_R \left( y^{(\ell)} \right),
	\end{align*}
	where we used that $0 \leq n \leq k + \ell - 1$. The infimum argument 
	gives the estimate on all Tensors $x,y \in \Tensor_R^{\bullet}(\lie{g})$ 
	and it extends to the completion such that
	\begin{equation*}
		p_R \left( z^n C_n(x, y) \right)
		\leq
		(16M q)_R(x) (16M q)_R(y)
		\frac{|z|^n}{2 \cdot (8M)^n}
	\end{equation*}
	and hence
	\begin{equation*}
		p_R(x \star_z y)
		\leq
		(16 M q)_R (x)
        (16 M q)_R (y)
		\sum\limits_{n=0}^{\infty}
        \frac{|z|^n}{2 \cdot (8M)^n}.
	\end{equation*}
	So the power series converges for all $z \in \mathbb{C}$ with
	$|z| < 8M$ and converges uniformly if $|z| \leq c M$ for $c < 8$.
	But then, the map \eqref{LCAna:Holomorphicity} converges on all open discs
	centered around $z = 0$, and it must therefore be entire.
\end{proof}
\begin{remark}[(Weakly) holomorphic maps with values in locally convex spaces]
	\label{LCAna:Rem:Holomorphicity} \hfill \\
	One could argue that the term ''holomorphic'' in a locally convex space 
	$V$ does not necessarily mean that a map has a absolutely convergent 
	Taylor expansion, but one should rather see the map 
	\eqref{LCAna:Holomorphicity} as a collection of paths $\mathbb{C} 
	\longrightarrow \widehat{\Sym}_R^{\bullet}(\lie{g})$ and ask for their 
	complex differentiability in the sense of a differential quotient. Of 
	course, this would be is a valid formulation of the word ''holomorphic'' 
	and this is also the standard definition for holomorphic maps with values 
	in locally convex spaces. According to this definition one calls a map 
	''weakly holomorphic'', if every continuous linear form 
	$\lambda \colon V \longrightarrow \mathbb{C}$ applied to it gives a 
	holomorphic map $\mathbb{C} \longrightarrow \mathbb{C}$. Using this 
	terminology, we would just have proven the map 
	\eqref{LCAna:Holomorphicity} to be \emph{weakly holomorphic}. Yet, we have 
	proven ''real'' holomorphicity, since in \cite[Theorem 3.31]{rudin:1991a} 
	Rudin proved the two notions of holomorphicity coincide in locally convex 
	spaces.
\end{remark}



\subsection{Representations}

We now want to identify the symmetric algebra with the Gutt star product with 
the the universal enveloping algebra $\algebra{U}(\lie{g}_z)$ with the scaled 
product.
\begin{definition}[The $\algebra{U}_R$-Topology]
	We denote by $\algebra{U}_R(\lie{g}_z)$ the locally convex algebra which we 
	get from $\algebra{U}(\lie{g}_z)$ by pulling back the $\Sym_R(\lie{g})$ 
	topology with the Poincar\'e-Birkholl-Witt isomophism $\mathfrak{q}$.
\end{definition}
We know that this algebra has the universal property that Lie algebra 
homomorphisms into associative algebras can be lifted to unital homomorphisms 
of associative algebras. As a commutative diagram, this reads
\begin{center}
    \begin{tikzpicture}
        \matrix (m)[
        matrix of math nodes,
        row sep=6em,
        column sep=7em
        ]
        {
          \mathcal{U}_R(\lie{g})
          & \Sym_R^{\bullet}(\lie{g}) \\
          \lie{g}
          & \algebra{A} \\
        };
        \draw
        [-stealth]
        (m-1-1) edge node [above] {$\lie{q}^{-1}$}
        (m-1-2) edge node [left] {$\Phi$}
        (m-2-2)
        (m-1-2) edge node [right] {$\widetilde{\Phi}$}
        (m-2-2)
        (m-2-1) edge node [left] {$\iota$}
        (m-1-1)
        (m-2-1) edge node [below] {$\phi$}
        (m-2-2);
    \end{tikzpicture}
\end{center}
where $\algebra{A}$ is the mentioned associative algebra. Since we endowed 
$\algebra{U}_R(\lie{g}_z)$ and $\Sym_R^{\bullet}(\lie{g})$ with a topology, we 
can now ask if the homomorphisms $\Phi$ and $\widetilde{\Phi}$ are continuous. 
This question is partly answered by the following result:
\begin{proposition}[Universal property]
    \label{LCAna:Prop:Semi-functoriality}%
    Let $\lie{g}$ be an AE-Lie algebra, $\algebra{A}$ an associative
    AE algebra and $\phi \colon \lie{g} \longrightarrow \algebra{A}$
    is a continuous Lie algebra homomorphism.  If $R \geq 1$, then the
    induced algebra homomorphisms $\Phi$ and $\widetilde{\Phi}$ are
    continuous.
\end{proposition}
\begin{proof}
    We define an extension of $\Phi$ on the whole tensor algebra
    again:
    \begin{equation*}
        \Psi \colon
        \Tensor_R^{\bullet}(\lie{g})
        \longrightarrow
        \algebra{A},
        \quad
        \Psi
        =
        \widetilde{\Phi} \circ \Symmetrizer
    \end{equation*}
    It is clear that if $\Psi$ is continuous on factorizing tensors,
    we will get the continuity of $\widetilde{\Phi}$ and of $\Phi$ via the
    infimum argument. So let $p$ be a continuous seminorm on
    $\algebra{A}$ with an asymptotic estimate $q$ and $\xi_1, \ldots,
    \xi_n \in \lie{g}$. Since $\phi$ is continuous, we find a
    continuous seminorm $r$ on $\lie{g}$ such that for all $\xi \in
    \lie{g}$ we have $q(\phi(\xi)) \leq r(\xi)$. Then we have
    \begin{align*}
        p \left(
        \Psi \left(
        \xi_1 \tensor \cdots \tensor \xi_n
        \right) \right)
        & =
        p \left(
        \widetilde{\Phi} \left(
        \xi_1 \star_z \cdots \star_z \xi_n
        \right) \right)
        \\
        & =
        p( \phi(\xi_1) \cdots \phi(\xi_n) )
        \\
        & \leq
        q( \phi(\xi_1) )
        \cdots
        q( \phi(\xi_n) )
        \\
        & \leq
        r(\xi_1) \cdots r(\xi_n)
        \\
        & \leq
        r_R(\xi_1 \tensor \cdots \tensor \xi_n),
    \end{align*}
    where the last inequality is true for all $R \geq 0$ and hence for all 
    $R \geq 1$.
\end{proof}
Although this is a nice result, our construction fails to be a universal object 
in the category of associative AE algebras, since the universal enveloping 
algebra endowed with our topology is \emph{not} AE in general. This is even 
very easy to see directly.
\begin{example}
    Take $\xi \in \lie{g}$, then we know that $\xi^{\tensor n} =
    \xi^{\ostar_z n} = \xi^n$ for $n \in \mathbb{N}$. 
    Let $R > 0$ and $p$ and $q$ be a continuous seminorms on $\lie{g}$ with 
    $q(\xi) \neq 0$, then we find
    \begin{equation}
        p_R(\xi^n)
        =
        n!^R p(\xi)^n
        =
        \frac{n!^R}{c^n} q(\xi)^n
    \end{equation}
    for $c = \frac{p(\xi)}{q(\xi)}$. But since $\frac{n!^R}{c^n}$ will always
    diverge for $n \rightarrow \infty$ we will never get an asymptotic
    estimate for $p$.
\end{example}
Another argument would be that we know that we can not have exponential 
functions in $\widehat{\Sym}_R^{\bullet}(\lie{g})$. If 
$\widehat{\Sym}_R^{\bullet}(\lie{g})$ (and hence $\algebra{U}_R(\lie{g}_z)$) 
were AE, then we would have an entire calculus which clearly includes 
exponential functions. Although the construction is not universal, we can draw 
a strong conclusion from Proposition~\ref{LCAna:Prop:Semi-functoriality}:
\begin{corollary}[Continuous Representations]
    \label{LCAna:Coro:ContinuousRepresentations}%
    Let $R \geq 1$ and $\mathcal{U}_R(\lie{g})$ the universal
    enveloping algebra of an AE-Lie algebra $\lie{g}$, then for every
    continuous representation $\phi$ of $\lie{g}$ into the bounded
    linear operators $\Bounded(V)$ on a Banach space $V$ the induced
    homomorphism of associative algebras $\Phi \colon
    \mathcal{U}(\lie{g}) \longrightarrow \Bounded(V)$ is continuous.
\end{corollary}
\begin{proof}
    This follows directly from
    Proposition~\ref{LCAna:Prop:Semi-functoriality} and $\Bounded(V)$
    being a Banach algebra.
\end{proof}
\begin{remark}
	From this, we get the special case that all finite-dimensional 
	representations of an AE-Lie algebra can be lifted to continuous 
	representations of $\algebra{U}_R(\lie{g}_z)$. 
	For infinite-dimensional Lie algebras, this statement will not be very 
	important, since there, one rather has strongly continuous 
	representations and no norm-continuous ones. Nevertheless, our 
	topology may help to think about continuous linear functionals on 
	$\algebra{U}_R(\lie{g}_z)$. We could then do GNS-representation 
	theory with it. This procedure would yield a representation of 
	$\algebra{U}_R(\lie{g}_z)$ on a (Pre-)Hilbert space and we could talk 
	about what strongly continuous representations of the universal 
	enveloping algebra should be. In this sense, the results of this 
	chapter may also open a door towards some new approaches in this field.
\end{remark}



\subsection{Functoriality}

Now let $\lie{g}, \lie{h}$ be two AE-Lie algebras. We know that a homomorphism 
of Lie algebras from $\lie{g}$ to $\algebra{U}(\lie{h}_z)$ would lift to a 
homomorphism $\algebra{U}(\lie{g}_z) \longrightarrow \algebra{U}(\lie{h}_z)$, 
if the latter one was AE, which is not the case. Yet, we would like to have 
this result and prove that our construction is functorial, but it will be 
more complicated than that. We draw the commutative diagram to clarify the 
situation:
\begin{center}
    \begin{tikzpicture}
        \matrix (m)[
        matrix of math nodes,
        row sep=3em,
        column sep=7em
        ]
        {
          \Sym_R^{\bullet}(\lie{g})
          & \Sym_R^{\bullet}(\lie{h}) \\
          \algebra{U}_R(\lie{g}_z)
          & \algebra{U}_R(\lie{h}_z) \\
          \lie{g}
          & \lie{h} \\
        };
        \draw
        [-stealth]
        (m-1-1) edge node [above] {$\widetilde{\Phi}_z$}
        (m-1-2)
        (m-2-1) edge node [left] {$\mathfrak{q}_z^{-1}$}
        (m-1-1)
        (m-2-1) edge node [above] {$\Phi_z$}
        (m-2-2)
        (m-2-2) edge node [right] {$\mathfrak{q}_z^{-1}$}
        (m-1-2)
        (m-3-1)	edge node [below] {$\phi$}
        (m-3-2)
        (m-3-1)	edge node [left] {$\iota_z$}
        (m-2-1)
        (m-3-2)	edge node [right] {$\iota_z$}
        (m-2-2);
    \end{tikzpicture}
\end{center}
Assume that $\phi$ is a continuous Lie algebra homomorphism. We want to know if 
$\Phi_z$ and $\widetilde{\Phi}_z$ will be continuous, too. Luckily, the answer 
is yes and our construction is functorial. For the proof, we will need the 
next lemma.
\begin{lemma}
    \label{LCAna:Lemma:LemmaPreContinuityN}%
    Let $\lie{g}$ be an AE-Lie algebra, $R \geq 1$, $z \in \mathbb{C}$ and $p$ 
    a continuous seminorm with an asymptotic estimate $q$. Then for every $n 
    \in \mathbb{N}$ and all $\xi_1, \ldots, \xi_n \in \lie{g}$ the estimate
    \begin{equation}
        \label{LCAna:LemmaPreContinuityN}
        p_R \left(
            \xi_1 \star_z \cdots \star_z \xi_n
        \right)
        \leq
        c^n n!^R
        q^n(\xi_1 \tensor \cdots \tensor \xi_n)
    \end{equation}
    holds with $c = 8 \E (|z| + 1)$.
\end{lemma}
\begin{proof}
    We start with a continuous seminorm $p$:
    \begin{align}
        \nonumber
        p_R \big(
            \xi_1 \star_z 
        &
            \cdots \star_z \xi_n
        \big)
        =
        p_R \Bigg(
        \sum\limits_{\ell = 0}^{n-1}
        \sum\limits_{\substack{
			1 \leq j \leq n-1 \\
			i_j \in \{0, \ldots, j\} \\
			\sum_{j = 1}^{n - 1} i_j = \ell
		}}
		z^{i_{n-1}}
		C_{i_{n-1}}
		\left(
			\ldots z^{i_2} C_{i_2}
			\left(
				z^{i_1} C_{i_1}
				\left( \xi_1, \xi_2 \right)
				, \xi_3
			\right)
			\ldots, \xi_n
		\right)
        \Bigg)
        \\
        \nonumber
        & \leq
        \sum\limits_{\ell = 0}^{n-1}
        (n - \ell)!^R
        \sum\limits_{\substack{
			1 \leq j \leq n-1 \\
			i_j \in \{0, \ldots, j\} \\
			\sum_{j = 1}^{n - 1} i_j = \ell
		}}
        p^{n - \ell} \Big(
		z^{i_{n-1}}
		C_{i_{n-1}}
		\left(
			\ldots z^{i_2} C_{i_2}
			\left(
				z^{i_1} C_{i_1}
				\left( \xi_1, \xi_2 \right)
				, \xi_3
			\right)
			\ldots, \xi_n
		\right)
		\Big)
        \\
        \nonumber
        & \leq
        \sum\limits_{\ell = 0}^{n-1}
        (n - \ell)!^R
        \sum\limits_{\substack{
			1 \leq j \leq n-1 \\
			i_j \in \{0, \ldots, j\} \\
			\sum_{j = 1}^{n - 1} i_j = \ell
		}}
        |B_{i_{n-1}}^*| \cdots |B_{i_1}^*|
        |z|^{i_{n-1}} \cdots |z|^{i_1}
        \\
        \nonumber
        & \quad \cdot
        \binom{1}{i_1} \binom{2 - i_1}{i_2}
        \cdots
        \binom{n - 1 - i_1 - \cdots i_{n-2}}{i_{n-1}}
        \frac{1}{2! 3 ! \cdots n!}
        \sum\limits_{\sigma_1 \in S_2, \ldots, \sigma_{n-1} \in S_n}
        \\
        & \quad \cdot
        \label{LCAna:PreContinuityIntermediateN}
        p^{n - i_1 - \cdots i_{n-1}}
        \left( 
         	\left[ w\left( \xi_1, \ldots, \xi_n \right) \right] 
        	\right).
    \end{align}
    In the last step, we iterated the $C_{i_j}$-operators. They are always 
    applied to a homogeneous symmetric tensor with a vector and hence always 
    give back a symmetrized sum of homogeneous symmetric tensors of the same 
    degree and with the same coefficients. $w[\cdots]$ denotes a symmetric 
    product of nested Lie bracket expressions involving all $\xi_i$.
    We can apply the AE property to it and get $q(\xi_1) \cdots q(\xi_n)$. Thus 
    the sum over the $\sigma_j$ vanishes with the inverse factorials.
    By using the fact that $|B_m^*| \leq m!$ for all $m \in
    \mathbb{N}$ and grouping together the powers of $|z|$, we find
    \begin{align*}
        &p_R \left(
            \xi_1 \star_z \cdots \star_z \xi_n
        \right) \\
        & \quad \ot{(a)}{\leq}
        \sum\limits_{\ell = 0}^{n-1}
        (n - \ell)!^R
        \sum\limits_{\substack{
			1 \leq j \leq n-1 \\
			i_j \in \{0, \ldots, j\} \\
			\sum_{j = 1}^{n - 1} i_j = \ell
		}}
        |z|^{\ell}
        \frac{1!  (2 - i_1)! \cdots (n-1 - i_1 - \cdots - i_{n-2})!}
        {(1 - i_1)! \cdots (n-1 - i_1 - \cdots i_{n-1})!}
        q(\xi_1) \cdots q(\xi_n)
        \\
        &\quad\ot{(b)}{\leq}
        \sum\limits_{\ell = 0}^{n-1}
        (n - \ell)!^R
        \sum\limits_{\substack{
			1 \leq j \leq n-1 \\
			i_j \in \{0, \ldots, j\} \\
			\sum_{j = 1}^{n - 1} i_j = \ell
		}}
        |z|^{\ell}
        1^{i_1} 2^{i_2}
        \cdots (n-1)^{i_{n-1}}
        q(\xi_1) \cdots q(\xi_n)
        \\
        &\quad\ot{(c)}{\leq}
        \sum\limits_{\ell = 0}^{n-1}
        (n - \ell)!^R
        \sum\limits_{\substack{
			1 \leq j \leq n-1 \\
			i_j \in \{0, \ldots, j\} \\
			\sum_{j = 1}^{n - 1} i_j = \ell
		}}
        |z|^{\ell}
        n^{\ell}
        q(\xi_1) \cdots q(\xi_n)
        \\
        &\quad\ot{(d)}{\leq}
        \sum\limits_{\ell = 0}^{n-1}
        (n - \ell)!^R
        \sum\limits_{\substack{
			1 \leq j \leq n-1 \\
			i_j \in \{0, \ldots, j\} \\
			\sum_{j = 1}^{n - 1} i_j = \ell
		}}
        |z|^{\ell} (2 \E)^n \ell!
        q(\xi_1) \cdots q(\xi_n).
    \end{align*}
    In (a), the factorials coming from the Bernoulli numbers cancelled out with 
    the the $i_j$ from the binomial coefficients and in (b) we used
    \begin{equation*}
    		\frac{(k - i_1 - \cdots - i_{k-1})!}
    		{(k - i_1 - \cdots - i_k)!}
    		\leq
    		k^{i_k}.
    \end{equation*}
    We can estimate the product of all those expressions by $(n-1)^{i_1 + 
    \cdots + i_{n-1}}$ and this by $n^\ell$, since the sum over all $i_j$ 
    equals $\ell$. In the last step (d) we used $n^{\ell} \leq \E^n
    \frac{n!}{(n-\ell)!} = \E^n \binom{n} {\ell} \ell! \leq \E^n 2^n
    \ell!$. But now we can simply estimate $|z|^{\ell} \leq (|z| +
    1)^n$ and $(n - \ell)!^R \ell! \leq n!^R$ for $R \geq 1$. We just
    need to count the number of summands and get
    \begin{align*}
        p_R \left(
            \xi_1 \star_z \cdots \star_z \xi_n
        \right)
        & \leq
        n!^R (2 \E)^n (|z| + 1)^n
        q(\xi_1) \cdots q(\xi_n)
        \sum\limits_{\ell = 0}^{n-1}
        \sum\limits_{\substack{
			1 \leq j \leq n-1 \\
			i_j \in \{0, \ldots, j\} \\
			\sum_{j = 1}^{n - 1} i_j = \ell
		}}
		1
        \\
        &\ot{(a)}{\leq}
        n!^R (2 \E)^n (|z| + 1)^n
        q(\xi_1) \cdots q(\xi_n)
        \sum\limits_{\ell = 0}^{n-1}
        \binom{n - 1 + \ell - 1}{\ell - 1}
        \\
        &\ot{(b)}{\leq}
        n!^R (2 \E)^n (|z| + 1)^n
        q(\xi_1) \cdots q(\xi_n)
        2^{2n}
        \\
        &\leq
        c^n n!^R q^n(\xi_1 \tensor \cdots \tensor \xi_n),
    \end{align*}
    with $c = 8 \E (|z| + 1)$. In ($a$) the estimate for the big sum
    is the following: for every $j = 1, \ldots, n-1$ we have surely
    $i_j \in \{0, 1, \ldots, n-1\}$ and the sum of all the $i_j$ is
    $\ell$. If we forget about all other restrictions, we will just get
    more terms. But then the number of summands is same as there
    are ways to distribute $\ell$ items on $n-1$ places, which is
    given by $\binom{n - 1 + \ell - 1}{\ell - 1}$. Then in ($b$) we
    use
    \begin{equation*}
        \binom{n - 1 + \ell - 1}{\ell - 1} \leq \binom{2 n}{\ell - 1}
    \end{equation*}
    with the binomial coefficient being zero for $\ell = 0$. Then it
    is just the standard estimate for binomial coefficients via the
    sum over all $\ell$.
\end{proof}
\begin{proposition}[Functoriality]
	\label{LCAna:Prop:Functoriality}
	Let $R \geq 1$, $\lie{g}, \lie{h}$ be AE-Lie algebras and $\phi \colon
	\lie{g} \longrightarrow \lie{h}$ a continuous homomorphism between them.
	Then it lifts to a continuous unital homomorphism of locally convex
	algebras $\Phi_z \colon \algebra{U}_R(\lie{g}_z) \longrightarrow
	\algebra{U}_R(\lie{h}_z)$.
\end{proposition}
\begin{proof}
	First, if $\phi \colon \lie{g} \longrightarrow \lie{h}$ is continuous, 
	then for every continuous seminorm $q$ on $\lie{h}$, we have a continuous 
	seminorm $r$ on $\lie{g}$ such that for all $\xi \in \lie{g}$
	\begin{equation*}
		q\left( \phi(\xi) \right)
		\leq
		r(\xi).
	\end{equation*}
	Second, we define $\Psi_z$ on factorizing tensors via
	\begin{equation*}
		\Psi_z \colon
		\Tensor_R^{\bullet}(\lie{g})
		\longrightarrow
		\Sym_R^{\bullet}(\lie{h})
		, \quad
		\Psi_z
		=
		\widetilde{\Phi}_z \circ
		\Symmetrizer
	\end{equation*}
	and extend it linearly to $\Tensor_R^{\bullet}(\lie{g})$. Clearly, 
	$\Phi_z$ and $\widetilde{\Phi}_z$ will be continuous if $\Psi_z$ is 
	continuous. From this, we get for a seminorm $p$ on $\lie{h}$, an 
	asymptotic estimate $q$ and $\xi_1, \ldots, \xi_n$
	\begin{align*}
		p_R\left(
			\Psi_z \left(
				\xi_1 \tensor \cdots \tensor \xi_n
			\right)
		\right)
		& =
		p_R \left(
			\phi \left( \xi_1 \right)
			\star_z \cdots \star_z
			\phi \left( \xi_1 \right)
		\right)
		\\
		& \leq
		c^n n!^R
		q \left( \phi \left( \xi_1 \right) \right)
		\cdots
		q \left( \phi \left( \xi_n \right) \right)
		\\
		& \leq
		c^n n!^R
		r \left( \xi_1 \right)
		\cdots
		r \left( \xi_n \right)
		\\
		& =
		(c r)_R\left( 
			\xi_1 \tensor \ldots \tensor \xi_n
		\right).
	\end{align*}
	Again, we use the infimum argument and we have the estimate on all tensor 
	in $\Tensor_R^{\bullet}(\lie{g})$. It extends to the completion and the 
	statement is proven.
\end{proof}



\section{Alternative topologies and an optimal result}
\label{sec:chap5_Optimality}

In this section we set the formal parameter $z = 1$ and make some 
observations. So far, we found a topology on $\Sym_R^{\bullet}(\lie{g})$ which 
gives a continuous star product and which has a reasonably large completion, 
but it is always fair to ask if we can do better than that: we have seen that 
our completed algebra will not contain exponential series, which would be a 
very good thing to have. So is it possible to put another locally convex 
topology on $\Sym_R^{\bullet}(\lie{g})$ which gives a completion with 
exponentials? The answer is no, at least under mild additional assumptions. 
\begin{proposition}[Optimality of the $\Tensor_R$-topology]
	\label{LCAna:Prop:NoBetterTopology}
	Let $\lie{g}$ be an AE Lie algebra in which one has elements $\xi, \eta$ 
	for which the Baker-Campbell-Hausdorff series does not converge. 
	Then there is no locally convex topology on $\Sym^{\bullet}(\lie{g})$ 
	such that all of the following things are fulfilled:
	\begin{propositionlist}
		\item
		The Gutt star product $\star_G$ is continuous.
		\item
		For every $\xi \in \lie{g}$ the series $\exp(\xi)$ converges 
		absolutely in the completion of $\Sym^{\bullet}(\lie{g})$.
		\item
		For all $n \in \mathbb{N}$ the projection and inclusion maps with 
		respect to the graded structure
		\begin{equation*}
			\Sym^{\bullet}(\lie{g})
	    		\ot{$\pi_n$}{\longrightarrow}
    	    		\Sym^n(\lie{g})
	    	    	\ot{$\iota_n$}{\longrightarrow}
	    		\Sym^{\bullet}(\lie{g})
		\end{equation*}
		are continuous.
	\end{propositionlist}
\end{proposition}
First of all, we should make clear what ''the Baker-Campbell-Hausdorff series 
does not converge'' actually means. This may be clear for a finite-dimensional 
Lie algebra, but in the locally convex setting, it is not that obvious. For 
simplicity, we assume our local convex space to be complete in the 
following, since we can always achieve this be completing it. First, we note 
here that a net or a sequence in a locally convex space is  convergent [or 
Cauchy], if and only if it is convergent [or Cauchy] with respect 
to all $p \in \algebra{P}$. Quite similar to a normed space, we can make the 
following definition.
\begin{definition}
	\label{Def:RadiusOfConvergenceLCS}
	Let $V$ be a locally convex vector space, $\algebra{P}$ the set of 
	continuous seminorms, $p \in \algebra{P}$ and 
	$\alpha = (\alpha_n)_{n \in \mathbb{N}}\subseteq V$ a sequence in $V$. 
	We set
	\begin{equation*}
		\rho_p(\alpha)
		=
		\left(
			\limsup_{n \longrightarrow \infty}
			\sqrt[n]{p \left(\alpha_n \right)}
		\right)^{-1}
	\end{equation*}
	where $\rho_p(\alpha) = \infty$ if $\limsup_{n \longrightarrow \infty} 
	\sqrt[n]{p \left(\alpha_n \right)} = 0$ as usual.
\end{definition}
From this, we immediately get the two following lemmas.
\begin{lemma}[Root test in locally convex spaces]
	\label{LCAna:Lemma:RootTest}
	Let $V$ be a complete locally convex vector space, $p \in \algebra{P}$ 
	and $\alpha = (\alpha_n)_{n \in \mathbb{N}} \subseteq V$ a sequence. 
	Then, if $\rho_p(\alpha) > 1$, the series
	\begin{equation*}
		\mathcal{S}_n(\alpha)
		=
		\sum\limits_{j = 0}^n
		\alpha_j
	\end{equation*}
	converges absolutely with respect to $p$. If, conversely, this
	series convegres with respect to $p$, then we have 
	$\rho_p(\alpha) \geq 1$.	
\end{lemma}
\begin{proof}
	The proof is completely analogous to the one in finite dimensions.
\end{proof}
\begin{lemma}
	\label{LCAna:Lemma:PowerSeriesConvAbs}
	Let $V$ be a complete locally convex vector space, $p \in \algebra{P}$, 
	$\alpha = (\alpha_n)_{n \in \mathbb{N}} \subseteq V$ a sequence and
	$M > 0$. Then, if the power series
	\begin{equation*}
		\lim_{n \longrightarrow \infty}
		\sum\limits_{j = 0}^n
		\alpha_j z^j
	\end{equation*}
	converges with respect to $p$ for all $z \in \mathbb{C}$ with $|z| \leq M$, 
	it converges absolutely with respect to $p$ for all $z \in \mathbb{C}$ with 
	$|z| < M$.
\end{lemma}
\begin{proof}
	Like in the finite-dimensional setting, we use the root test: Convergence 
	for $|z| \leq M$ means $\rho_p(\alpha_z) \geq 1$, where we have set 
	$\alpha_z = (\alpha_n z^n)_{n \in \mathbb{N}}$. Hence, for every $z' < z$ 
	we get $\rho_p(\alpha_{z'}) > 1$ and absolute convergence by Lemma 
	\ref{LCAna:Lemma:RootTest}.
\end{proof}
But this means, that a power series $\alpha_z$ in a locally convex space have 
have $\rho_p(\alpha_z) = \infty$ for all $p \in \algebra{P}$: if there was a $p 
\in \algebra{P}$ with a finite radius of convergence, we could take a multiple 
of $p$ in order to get a seminorm with arbitrarily small radius of convergence. 
Hence $\alpha_z$ could not converge for any $z \neq 0$. This helps us to make 
clear, what ''BCH does not converge'' can be interpreted, since we can read it 
as a power series in two variables:
\begin{equation*}
	\bch{t \xi}{s \eta}
	=
	\sum\limits_{a,b = 0}^{\infty}
	t^a s^b
	\bchparts{a}{b}{\xi}{\eta}.
\end{equation*}
So if it converges for $\xi$ and $\eta$, then it converges absolutely for all 
$t \xi$ and $s \eta$ with $t,s \in [0, 1)$. If it even converges for all $t 
\xi$ and $s \eta$ with $t, s \in \mathbb{K}$, then it converges absolutely for 
all $t, s$. If this is the case, we can reorder the sums as we like to, and the 
series
\begin{equation*}
	\sum\limits_{n = 0}^N
	\bchpart{n}{\xi}{\eta}
\end{equation*}
converges if and only if the series
\begin{equation*}
	\bch{t \xi}{s \eta}
	=
	\sum\limits_{a = 0}^{\infty}
	\sum\limits_{b = 0}^{\infty}
	\bchparts{a}{b}{\xi}{\eta}
\end{equation*}
converges. Now we can prove a Lemma, from which Proposition 
\ref{LCAna:Prop:NoBetterTopology} will follow immediately.
\begin{lemma}
	Let $\lie{g}$ be an AE Lie algebra and $\Sym^{\bullet}(\lie{g})$ is 
	endowed with a locally convex topology, such that the conditions $(i) - 
	(iii)$ from Proposition~\ref{LCAna:Prop:NoBetterTopology} are fulfilled. 
	Then the Baker-Campbell-Hausdorff series converges absolutely for all 
	$\xi, \eta \in \lie{g}$.
\end{lemma}
\begin{proof}
	First, we complete the algebra to $\widehat{\Sym}^{\bullet}(\lie{g})$.
	We will need the projection $\pi_1$ to the Lie algebra. Take 
	$\xi, \eta \in 	\lie{g}$. Now, since the the Gutt star product is 
	continuous and the exponential series is absolutely convergent for 
	all $\xi, \eta \in \lie{g}$, we get for $t, s \in \mathbb{K}$
	\begin{align*}
		\pi_1 \left( \exp(t \xi) \star \exp(s \eta) \right)
		& =
		\pi_1
		\left(
			\lim_{N \rightarrow \infty}
			\left(
				\sum\limits_{n=0}^N
				\frac{t^n \xi^n}{n!}
			\right)
			\star
			\lim_{M \rightarrow \infty}
			\left(
				\sum\limits_{m=0}^M
				\frac{s^m \eta^m}{m!}
			\right)
		\right)
		\\
		& \ot{(a)}{=}
		\pi_1
		\left(
			\lim_{N \rightarrow \infty}
			\lim_{M \rightarrow \infty}
			\left(
				\sum\limits_{n=0}^N
				\frac{t^n \xi^n}{n!}
			\right)
			\star_G
			\left(
				\sum\limits_{m=0}^M
				\frac{s^m \eta^m}{m!}
			\right)
		\right)
		\\
		& \ot{(b)}{=}
		\lim_{N \rightarrow \infty}
		\lim_{M \rightarrow \infty}
		\pi_1
		\left(	
			\left(
				\sum\limits_{n=0}^N
				\frac{t^n \xi^n}{n!}
			\right)
			\star_G
			\left(
				\sum\limits_{m=0}^M
				\frac{s^m \eta^m}{m!}
			\right)
		\right)
		\\
		& \ot{(c)}{=}
		\lim_{N \rightarrow \infty}
		\lim_{M \rightarrow \infty}
		\sum\limits_{n,m=0}^{N, M}
		\bchparts{t \xi}{s \eta}{n}{m}
	\end{align*}
	where we used the continuity of the star product in (a), the continuity of 
	the projection in (b) and evaluated the projection in (c). Since 
	$\exp(t \xi)$ and $\exp(s \eta)$ are elements in the completion, their 
	star product exists and hence the double series at the end of this 
	equation converges for any two elements $\xi, \eta \in \lie{g}$. But now 
	we can use the result that in this setting the BCH series converges 
	absolutely. We can rearrange the terms and get the convergence of
	\begin{equation*}
		\sum\limits_{n = 1}^N
		\bchpart{n}{t \xi}{s \eta}.
	\end{equation*}
	Therefore, the BCH series must converge globally.
\end{proof}
Obviously, this proves Proposition~\ref{LCAna:Prop:NoBetterTopology}.


Now we want to use a result due to Wojty\'nski \cite{wojtynski:1998a}, who 
showed that for Banach-Lie algebras, global convergence of the BCH series is 
equivalent to the fact that for any $\xi$ we have
\begin{equation*}
	\norm{ 
		\left( \ad_{\xi} \right)^n 
	}^{\frac{1}{n}}
	\stackrel{n \rightarrow \infty}{\longrightarrow}
	0.
\end{equation*}
A Banach-Lie algebra with this property is sometimes called quasi-nilpotent, 
radical or nil, see for example \cite{mueller:1994a} for various 
generalizations of nilpotency in the case of Banach algebras.
For finite-dimensional Lie algebras, quasi-nilpotency implies nilpotency. 
Hence for a finite-dimensional Lie algebra $\lie{g}$, BCH is globally 
convergent if and only if $\lie{g}$ is nilpotent.


From this, we see that at least for ''non-quasi-nilpotent'' Banach-Lie 
algebras, our result is in some sense optimal, at least if we want the grading 
structure to compatible with the topology.
\begin{remark}[Another topology in $\algebra{U}(\lie{g})$]
    \label{Rem:LCAnaBCHConvergence}
    In \cite{pflaum.schottenloher:1998a} Schottenloher and Pflaum mention an 
    alternative topology on the universal enveloping algebra for 
    finite-dimensional Lie algebras: they take the coarsest locally convex 
    topology, such that all finite-dimensional representations of $\lie{g}$ 
    extend to continuous algebra homomorphisms. This topology is in fact even 
    locally m-convex and has therefore an entire holomorphic calculus. In 
    particular, the completion will contain exponential functions for all Lie 
    algebra elements. Therefore, as we have seen in 
    Proposition~\ref{LCAna:Prop:NoBetterTopology}, it can not respect the 
    grading structure, as our topology does. The $\Tensor_R$-topology must 
    hence be different from that. As we have seen in 
    Corollary~\ref{LCAna:Coro:ContinuousRepresentations}, it is finer for 
    $R \geq 1$, and since the topologies are different, it is even strictly 
    finer. One could argue that the $R$-topology is ''just'' locally convex, 
    but its advantage (for our purpose) is that the grading is necessary for 
    the holomorphic dependence on the formal parameter which is a feature that 
    we want.
\end{remark}
